---
title: "Clade Disparity"
output: html_notebook
---
# Figure S3
Measuring the disparity of clades. There are a lot of analyses leading Up to this plot. Everything from start to finish is here.

This will work like the community disparity analyses, except group by clade not community. 

There is no way to estimate variance for one species. I think Haeromys must be skipped.


```{r}
pacman::p_load(tidyverse, brms, tidybayes, patchwork, modelr)
scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = na.rm)) / sd(x, na.rm)
load("Species_Lists.Rdata")

# Species Lists
echiothrix <- c("Echiothrix_centrosa", "Echiothrix_leucura",  "Gracillimus_radix", "Hyorhinomys_steumpkei", "Melasmothrix_naso",  "Paucidentomys_vermidax", "Sommeromys_macrorhinos", 
"Tateomys_macrocercus", "Tateomys_rhinogradoides", "Waiomys_mamasae")
bunomys <- c("Bunomys_andrewsi", "Bunomys_chrysocomus", "Bunomys_coelestis", "Bunomys_fratrorum", "Bunomys_penitus", "Bunomys_prolatus", "Bunomys_torajae", "Eropeplus_canus", "Lenomys_meyeri", "Paruromys_dominator", "Taeromys_callitrichus", "Taeromys_celebensis", "Taeromys_hamatus", "Taeromys_sp_katopasa", "Taeromys_tarae")
maxomys <- c("Crunomys_celebensis", "Maxomys_dollmani", "Maxomys_hellwaldii", "Maxomys_musschenbroekii", "Maxomys_wattsi")
margaretamys <- c("Margaretamys_elegans", "Margaretamys_parvus")
rattus <- c("Rattus_botanus", "Rattus_facetus", "Rattus_hoffmani", "Rattus_marmosurus", "Rattus_mollicomulus", "Rattus_xanthurus")
haeromys <- c("Haeromys_minahassae")

load("Species_Extant.Rdata")


```

# Cranium 


## Data and Function 
Function taken from Community Variance Function
```{r}
cran <- read_csv("Cranial_Data/Cranial_36axes_Fitted.csv")

get_cran <- function(sp, data, mountain) {
data %>% 
  filter(Species %in% {{sp}}) %>%
  #select(!Species) %>%
  select(!.row) %>%
  group_by(.draw) %>% 
  mutate( vcPC1 = (var(cPC1) * 0.2041), vcPC2 = (var(cPC2) * 0.1479), vcPC3 = (var(cPC3) * 0.0644), vcPC4 = (var(cPC4) * 0.0604), vcPC5 = (var(cPC5) * 0.0434), vcPC6 = (var(cPC6) * 0.0381), vcPC7 = (var(cPC7) * 0.0367), vcPC8 = (var(cPC8) * 0.0334), vcPC9 = (var(cPC9) * 0.0302), vcPC10 = (var(cPC10) * 0.0273), vcPC11 = (var(cPC11) * 0.0233), vcPC12 = (var(cPC12) * 0.0207), vcPC13 = (var(cPC13) * 0.0179), vcPC14 = (var(cPC14) * 0.0170), vcPC15 = (var(cPC15) * 0.0162), vcPC16 = (var(cPC16) * 0.0152), vcPC17 = (var(cPC17) * 0.0142), vcPC18 = (var(cPC18) * 0.0123), vcPC19 = (var(cPC19) * 0.0117), vcPC20 = (var(cPC20) * 0.0106), vcPC21 = (var(cPC21) * 0.0098), vcPC22 = (var(cPC22) * 0.0095), vcPC23 = (var(cPC23) * 0.0090), vcPC24 = (var(cPC24) * 0.0080), vcPC25 = (var(cPC25) * 0.0078), vcPC26 = (var(cPC26) * 0.0075), vcPC27 = (var(cPC27) * 0.0072), vcPC28 = (var(cPC28) * 0.0069), vcPC29 = (var(cPC29) * 0.0063), vcPC30 = (var(cPC30) * 0.0059), vcPC31 = (var(cPC31) * 0.0054), vcPC32 = (var(cPC32) * 0.0052), vcPC33 = (var(cPC33) * 0.0051), vcPC34 = (var(cPC34) * 0.0046), vcPC35 = (var(cPC35) * 0.0043), vcPC36 = (var(cPC35) * 0.0038), vcCsize = var(cCsize)) %>%
    mutate(cv_wei = vcPC1 + vcPC2 + vcPC3 + vcPC4 + vcPC5 + vcPC6 + vcPC7 + vcPC8 + vcPC9 + vcPC10 + vcPC11 + vcPC12 + vcPC13 + vcPC14 + vcPC15 + vcPC16 + vcPC17 + vcPC18 + vcPC19 + vcPC20 + vcPC21 + vcPC22 + vcPC23 + vcPC24 + vcPC25 + vcPC26 + vcPC27 + vcPC28 + vcPC29 + vcPC30 + vcPC31 + vcPC32 + vcPC33 + vcPC34 + vcPC35 + vcPC36 ) %>% 
    mutate(cPC_wei = (cPC1 * 0.2041) + (cPC2 * 0.1479) +  (cPC3 * 0.0644) +  (cPC4 * 0.0604) +  (cPC5 * 0.0434) +  (cPC6 * 0.0381) +  (cPC7 * 0.0367) +  (cPC8 * 0.0334) +  (cPC9 * 0.0302) +  (cPC10 * 0.0273) +  (cPC11 * 0.0233) +  (cPC12 * 0.0207) +  (cPC13 * 0.0179) +  (cPC14 * 0.0170) +  (cPC15 * 0.0162) +  (cPC16 * 0.0152) + (cPC17 * 0.0142) + (cPC18 * 0.0123) + (cPC19 * 0.0117) + (cPC20 * 0.0106) + (cPC21 * 0.0098) + (cPC22 * 0.0095) + (cPC23 * 0.0090) + (cPC24 * 0.0080) + (cPC25 * 0.0078) + (cPC26 * 0.0075) + (cPC27 * 0.0072) + (cPC28 * 0.0069) + (cPC29 * 0.0063) + (cPC30 * 0.0059) + (cPC31 * 0.0054) + (cPC32 * 0.0052) + (cPC33 * 0.0051) + (cPC34 * 0.0046) + (cPC35 * 0.0043) + (cPC36 * 0.0038)) %>% 
    select(.draw, vcCsize, cv_wei, Species, cPC_wei, cCsize) %>% 
    add_column(clade = {{mountain}})
}
```

## Cranium Shape Clade Variance

```{r}
c1 <- get_cran(echiothrix, cran, "Echiothrix")
c2 <- get_cran(bunomys, cran, "Bunomys") 
c3 <- get_cran(margaretamys, cran, "Margaretamys") 
c4 <- get_cran(maxomys, cran, "Maxomys")
c5 <- get_cran(rattus, cran, "Rattus")
c6 <- get_cran(haeromys,  cran, "Haeromys")
cct <- bind_rows(c1, c2, c3, c4, c5, c6)
write_csv(cct, "Cranial_Data/Clade_Cranial_Variance_Weighted.csv")
```

```{r}
p1 <- cct %>% 
ggplot(aes(y = factor(clade), x = cv_wei)) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  labs(x="Sum of Variance", y = "", fill = "Clade") +
  theme_classic() + theme(legend.position = "none",
                     panel.grid.major.y = element_line( size=.1, color="black" ))

p2 <- cct %>% ggplot(aes(y = factor(clade), x = cPC_wei, fill = Species)) +
  scale_fill_manual(values = c(rep("grey", 39))) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.2) +
  labs( y = "") +
  theme_classic() +
  theme(legend.position = "none",
        axis.text.y=element_blank(),
        panel.grid.major.y = element_line( size=.1, color="black" )) 

p1 + p2 + plot_layout(widths = c(1,2)) + plot_annotation(title = "Cranial Shape Disparity")
```

#Dentary

## Data and Function

```{r}
dent <- read_csv("Dentary_Data/Dentary_20axes_Fitted.csv")

get_dent <- function(sp, data, mountain) {
data %>% 
  filter(Species %in% {{sp}}) %>%
  #select(!Species) %>%
  select(!.row) %>%
  group_by(.draw) %>% 
    mutate(vdPC1 = (var(dPC1) * 0.2821), vdPC2 = (var(dPC2) * 0.1529), vdPC3 = (var(dPC3) * 0.1424), vdPC4 = (var(dPC4) * 0.0693), vdPC5 = (var(dPC5) * 0.0548), vdPC6 = (var(dPC6) * 0.0393), vdPC7 = (var(dPC7) * 0.0345), vdPC8 = (var(dPC8) * 0.0269), vdPC9 = (var(dPC9) * 0.0241), vdPC10 = (var(dPC10) * 0.0212), vdPC11 = (var(dPC11) * 0.0173), vdPC12 = (var(dPC12) * 0.0164), vdPC13 = (var(dPC13) * 0.0126), vdPC14 = (var(dPC14) * 0.0117), vdPC15 = (var(dPC15) * 0.0102), vdPC16 = (var(dPC16) * 0.0097), vdPC17 = (var(dPC17) * 0.0089), vdPC18 = (var(dPC18) * 0.0082), vdPC19 = (var(dPC19) * 0.0066), vdPC20 = (var(dPC20) * 0.0059), vdCsize = var(dCsize)) %>%
    mutate(dv_wei =  vdPC1 + vdPC2 + vdPC3 + vdPC4 + vdPC5 + vdPC6 + vdPC7 + vdPC8 + vdPC9 + vdPC10 + vdPC11 + vdPC12 + vdPC13 + vdPC14 + vdPC15 + vdPC16 + vdPC17 + vdPC18 + vdPC19 + vdPC20) %>% 
    mutate(dPC_wei = (dPC1 + 0.2821) + (dPC2 * 0.1529) + (dPC3 * 0.1424) +  (dPC4 * 0.0693) +  (dPC5 * 0.0548) +  (dPC6 * 0.0393) +  (dPC7 * 0.0345) +  (dPC8 * 0.0269) +  (dPC9 * 0.0241) +  (dPC10 * 0.0212) +  (dPC11 * 0.0173) +  (dPC12 * 0.0164) +  (dPC13 * 0.0126) +  (dPC14 * 0.0117) +  (dPC15 * 0.0102) +  (dPC16 * 0.0097) +  (dPC17 * 0.0089) +  (dPC18 * 0.0082) +  (dPC19 * 0.0066) +  (dPC20 * 0.0059)) %>% 
    select(.draw, vdCsize, dv_wei, dPC_wei, Species, dCsize) %>% 
    add_column(clade = {{mountain}})
}
```

## Dentary Shape Clade
```{r}
c1 <- get_dent(echiothrix,    dent, "Echiothrix")
c2 <- get_dent(bunomys,       dent, "Bunomys") 
c3 <- get_dent(margaretamys,  dent, "Margaretamys") 
c4 <- get_dent(maxomys,       dent, "Maxomys")
c5 <- get_dent(rattus,        dent, "Rattus")
c6 <- get_dent(haeromys,      dent, "Haeromys")
ddt <- bind_rows(c1, c2, c3, c4, c5, c6)
write_csv(cct, "Dentary_Data/Clade_Dentary_Variance_Weighted.csv")
```

```{r}
p3 <- ddt %>% ggplot(aes(y = factor(clade), x = dv_wei)) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  labs(x="Sum of Variance", y = "", fill = "Clade") +
  theme_classic() + theme(legend.position = "none",
                     panel.grid.major.y = element_line( size=.1, color="black" ))

p4 <- ddt %>%  
  ggplot(aes(y = factor(clade), x = dPC_wei, fill = Species)) +
  scale_fill_manual(values = c(rep("grey", 39))) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.2) +
  labs( y = "") +
  theme_classic() +
  theme(legend.position = "none",
        axis.text.y=element_blank(),
        panel.grid.major.y = element_line( size=.1, color="black" ))  

p1 + p2 + plot_layout(widths = c(1,2)) + plot_annotation(title = "Dentary Shape Disparity")
```

# External Measurements

## Data and Function
```{r}
ext <- read_csv("External_Measurement_Data/External_Fitted.csv")

get_ext <- function(sp, data, mountain) {
data %>% 
  filter(Species %in% {{sp}}) %>%
  #select(!Species) %>%
  select(!.row) %>%
  group_by(.draw) %>%  
  mutate(vHB = var(HB),
            vTail = var(rTail),
            vHF = var(rHF),
            vEar = var(rEar),
            vMass = var(lMass)) %>% 
  mutate(ext_sum = vHB + vTail + vHF + vEar + vMass) %>% 
  mutate(ext_scaled = ext_sum/5) %>% 
  add_column(clade = {{mountain}})
}

```
## External Clade
```{r}
c1 <- get_ext(echiothrix,    ext, "Echiothrix")
c2 <- get_ext(bunomys,       ext, "Bunomys") 
c3 <- get_ext(margaretamys,  ext, "Margaretamys") 
c4 <- get_ext(maxomys,       ext, "Maxomys")
c5 <- get_ext(rattus,        ext, "Rattus")
c6 <- get_ext(haeromys,      ext, "Haeromys")
eet <- bind_rows(c1, c2, c3, c4, c5, c6)
write_csv(eet, "External_Measurement_Data/Clade_External_Variance_Fitted.csv")
```

```{r}
p5 <- eet %>% ggplot(aes(y = factor(clade), x = vTail)) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  labs(x="Sum of Variance", y = "", fill = "Clade") +
  theme_classic() + theme(legend.position = "none",
                     panel.grid.major.y = element_line( size=.1, color="black" ))

p6 <- eet %>% 
  ggplot(aes(y = factor(clade), x = rTail, fill = Species)) +
  scale_fill_manual(values = c(rep("grey", 39))) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.2) +
  labs( y = "") +
  theme_classic() +
  theme(legend.position = "none",
        axis.text.y=element_blank(),
        panel.grid.major.y = element_line( size=.1, color="black" )) 

p5 + p6 + plot_layout(widths = c(1,2)) + plot_annotation(title = "Tail Disparity")
```

```{r}
p7 <- eet %>% ggplot(aes(y = factor(clade), x = vHB)) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  labs(x="Sum of Variance", y = "", fill = "Clade") +
  theme_classic() + theme(legend.position = "none",
                     panel.grid.major.y = element_line( size=.1, color="black" ))

p8 <- eet %>% 
  ggplot(aes(y = factor(clade), x = HB, fill = Species)) +
  scale_fill_manual(values = c(rep("grey", 39))) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.2) +
  labs( y = "") +
  theme_classic() +
  theme(legend.position = "none",
        axis.text.y=element_blank(),
        panel.grid.major.y = element_line( size=.1, color="black" )) 

p7 + p8 + plot_layout(widths = c(1,2)) + plot_annotation(title = "Head-Body Length Disparity")
```

```{r}
p9 <- eet %>% ggplot(aes(y = factor(clade), x = vHF)) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  labs(x="Sum of Variance", y = "", fill = "Clade") +
  theme_classic() + theme(legend.position = "none",
                     panel.grid.major.y = element_line( size=.1, color="black" ))

p10 <- eet %>% 
  ggplot(aes(y = factor(clade), x = rHF, fill = Species)) +
  scale_fill_manual(values = c(rep("grey", 39))) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.2) +
  labs( y = "") +
  theme_classic() +
  theme(legend.position = "none",
        axis.text.y=element_blank(),
        panel.grid.major.y = element_line( size=.1, color="black" )) 

pp1 <- p1 + p2 + plot_layout(widths = c(1,2)) + plot_annotation(title = "Hind Foot Length Disparity")
```


# Isotopes

## Data and Function

```{r}
iso <- read_csv("Isotope_Data/Isotope_Group_Level_Fitted.csv")

get_iso <- function(sp, data, mountain) {
data %>% 
  filter(Species %in% {{sp}}) %>%
  #select(!Species) %>%
  select(!.row) %>%
  group_by(.draw) %>%  
  mutate(vN15 = var(sN15),
        vC13 = var(sC13),
        vIso = (vN15 + vC13)/2,
        Iso = (sN15 + sC13)/2) %>% 
  add_column(clade = {{mountain}})
}
```

# Iso Clade Variance
```{r}
c1 <- get_iso(echiothrix,    iso, "Echiothrix")
c2 <- get_iso(bunomys,       iso, "Bunomys") 
c3 <- get_iso(margaretamys,  iso, "Margaretamys") 
c4 <- get_iso(maxomys,       iso, "Maxomys")
c5 <- get_iso(rattus,        iso, "Rattus")
c6 <- get_iso(haeromys,      iso, "Haeromys")
ist <- bind_rows(c1, c2, c3, c4, c5, c6)
write_csv(ist, "Isotope_Data/Clade_Isotope_Fitted.csv")
```


```{r}
p11 <- ist %>% ggplot(aes(y = factor(clade), x = vN15)) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  labs(x="Sum of Variance", y = "", fill = "Clade") +
  theme_classic() + theme(legend.position = "none",
                     panel.grid.major.y = element_line( size=.1, color="black" ))

p12 <- ist %>% 
  ggplot(aes(y = factor(clade), x = sN15, fill = Species)) +
  scale_fill_manual(values = c(rep("grey", 39))) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.2) +
  labs( y = "") +
  theme_classic() +
  theme(legend.position = "none",
        axis.text.y=element_blank(),
        panel.grid.major.y = element_line( size=.1, color="black" )) 

#pp1 <- 
p1 + p2 + plot_layout(widths = c(1,2)) + plot_annotation(title = "N15 Disparity")
```




#Combine and Save
```{r}
dat <- cct %>% right_join(ddt) %>% right_join(eet) %>% right_join(ist)
dat %>% write_csv("Clade_Varaince.csv")
rm(cct, ddt, ext, ist)
```

# Locomotor Variance
## Data and Function
```{r}
loc <- read_csv("Locomotion_Data/Locomotion_List.csv")

get_loc<- function(sp, data, mountain) {
data %>% 
  filter(Species %in% {{sp}}) %>%
  #select(!Species) %>%
  #select(!.row) %>%
 # group_by(.draw) %>%  
  mutate(vloc = var(Loc)) %>% 
  add_column(clade = {{mountain}})
}
```
## Loc Var
```{r}
c1 <- get_loc(echiothrix,    loc, "Echiothrix")
c2 <- get_loc(bunomys,       loc, "Bunomys") 
c3 <- get_loc(margaretamys,  loc, "Margaretamys") 
c4 <- get_loc(maxomys,       loc, "Maxomys")
c5 <- get_loc(rattus,        loc, "Rattus")
c6 <- get_loc(haeromys,      loc, "Haeromys")
lst <- bind_rows(c1, c2, c3, c4, c5, c6)
write_csv(lst, "Locomotion_Data/Clade_Locomotion_Var.csv")
```



#Plotting the Clade Fitted Varaince

```{r}
pacman::p_load(tidyverse, patchwork, tidybayes)
dat <- read_csv("Clade_Varaince.csv")
ldat <- read_csv("Locomotion_Data/Clade_Locomotion_Var.csv")
```

## Plotting Functions



```{r}
vplot <- function(var, xlab){
dat %>% 
    ggplot(aes(y = factor(clade), x = {{var}})) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  labs(x={xlab}, y = "") +
  theme_classic() + theme(legend.position = "none",
                     panel.grid.major.y = element_line( size=.1, color="black" ))
}

splot <- function(var, xlab){
  dat %>% 
    ggplot(aes(y = factor(clade), x = {{var}}, fill = Species)) +
    scale_fill_manual(values = c(rep("grey", 39))) +
    stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.2) +
    labs( x = {xlab}, y = "") +
    theme_classic() +
    theme(legend.position = "none",
          axis.text.y=element_blank(),
          panel.grid.major.y = element_line( size=.1, color="black" )) 
}
```



```{r}
p1 <-  vplot(cv_wei, "Cranial Shape Var.")
p2 <-  vplot(vcCsize, "Cranial Size Var.")
p3 <-  vplot(dv_wei, "Dentary Shape Var.")
p4 <-  vplot(vdCsize, "Dentary Size Var.")
p5 <-  vplot(vN15, "15N Var.")
p6 <-  vplot(vC13, "13C Var.")
p7 <-  vplot(vHB, "Head-Body Length Var.")
p8 <-  vplot(vMass, "log(Mass) Var.")
p9 <-  vplot(vTail, "Tail Length Var")
p10 <-  vplot(vHF, "Hind Foot Length Var.")
p11 <-  vplot(vEar, "Ear Length Var.")


vplot(vN15, "15N Var.")
vplot(vC13, "13C Var.")


s1 <-  splot(cPC_wei, "Cranial Shape")
s2 <-  splot(cCsize, "Cranial Size")
s3 <-  splot(dPC_wei, "Dentary Shape")
s4 <-  splot(dCsize, "Dentary Size.")
s5 <-  splot(sN15, "15N")
s6 <-  splot(sC13, "13C")
s7 <-  splot(HB, "Head-Body Length")
s8 <-  splot(lMass, "log(Mass)")
s9 <-  splot(rTail, "Tail Length")
s10 <-  splot(rHF, "Hind Foot Length")
s11 <-  splot(rEar, "Ear Length")
```
# Locomotor Var
```{r}
p12 <- lst %>% select(vloc, clade) %>% 
  ggplot(aes(y = clade, x = vloc)) +
  geom_point(shape = 15, size = 10,
             position = position_nudge(y = .28), color = "grey30") +
  geom_point(shape = 15, size = 10,
             position = position_nudge(y = .5), color = "grey30") +
  scale_y_discrete(drop = F) +
  scale_x_continuous(breaks = c(0, 0.2, 0.4, 0.6), limits = c(-.01, 0.61)) +
  labs(x="Locomotor Var.", y = "") +
  theme_classic() + 
  theme(legend.position = "none",
        panel.grid.major.y = element_line( size=.1, color="black" ))
p12

```

```{r}
s12 <- lst %>% 
  mutate(clade = as.factor(clade),
         mlt = rep(c(-0.13,0, 0.13), length.out = 39),
         Loc = as.numeric(Loc),
         Loc2 = Loc+mlt) %>% 
    ggplot(aes(x = clade, y = Loc2)) + 
  geom_dotplot(binaxis='y', 
               position = "dodge", 
               binwidth = 0.13, 
               colour = "grey30",
               fill = "grey30") + 
  scale_y_continuous(labels= c('Arboreal',
                               'General', 
                               'Terrestrial',
                               'Amphibious'), 
                     breaks=1:4) +
  coord_flip() +
  labs( y = 'Locomotor Mode', x = "") +
  theme_classic() + 
  theme(axis.text.y=element_blank(),
        axis.text.x = element_text(size = 6.5),
        panel.grid.major.y = element_line( size=.1, color="black" ))


s12

```


```{r}
layout <- "
ABBCDD
EFFGHH
IJJKLL
MNNOPP
QRRSTT
UVVWXX
"

p1 + s1 + p2 + s2 + p3 + s3 + p4 + s4 + p5 +s5 + p6 + s6 + p7 + s7 + p8 + s8 + p9 + s9 + p10 + s10 + p11 + s11 + p12 + s12 +
  plot_layout(design = layout, tag_level = 'new') + plot_annotation(tag_levels = list(c('A', '', 'B', '', 'C', '', 'D', '', 'E', '', 'F', '', 'G', '', 'H', '', 'I', '', 'J', '', 'K', '', 'L', '')))

ggsave("Plots/FigS3_Clade_Var_Plots.pdf", height = 23.25, width =12)
#without ear and loc
#ggsave("Clade_Var_Plots.pdf", height = 19.25, width =12)
```



```{r}
lst %>% 
  mutate(clade = as.factor(clade),
         mlt = rep(c(-0.025,0.025), length.out = 39),
         Loc = as.numeric(Loc),
         Loc2 = Loc+mlt) %>% 
    ggplot(aes(x = clade, y = Loc2)) + 
  geom_dotplot(binaxis='y', position = "dodge", binwidth = 0.04) + 
  scale_y_continuous(labels= c('Arboreal',
                               'General', 
                               'Terrestrial',
                               'Amphibious'), 
                     breaks=1:4) +
  coord_flip() +
  theme_classic() + 
  theme(axis.text.y=element_blank(),
        axis.text.x = element_text(size = 9),
        panel.grid.major.y = element_line( size=.1, color="black" ))



```

