---
title: "Clade Disparity"
date: "`r Sys.Date()`"
---
# Figure S3

Measuring and plotting the disparity of and among clades. There are a lot of analyses leading Up to this plot. Everything from start to finish is here.

This will work like the community disparity analyses, except group by clade not community. 

There is no way to estimate variance for one species. I think Haeromys must be skipped.

```{r}
pacman::p_load(here, tidyverse, brms, tidybayes, patchwork, modelr)
scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = na.rm)) / sd(x, na.rm)


here::i_am('Code/Models_Fitted_Variance.Rmd')

load(here("Species_Data", "Species_Lists.Rdata"))

# Species Lists
echiothrix <- c("Echiothrix_centrosa", "Echiothrix_leucura",  "Gracillimus_radix", "Hyorhinomys_steumpkei", "Melasmothrix_naso",  "Paucidentomys_vermidax", "Sommeromys_macrorhinos", 
"Tateomys_macrocercus", "Tateomys_rhinogradoides", "Waiomys_mamasae")
bunomys <- c("Bunomys_andrewsi", "Bunomys_chrysocomus", "Bunomys_coelestis", "Bunomys_fratrorum", "Bunomys_penitus", "Bunomys_prolatus", "Bunomys_torajae", "Eropeplus_canus", "Lenomys_meyeri", "Paruromys_dominator", "Taeromys_callitrichus", "Taeromys_celebensis", "Taeromys_hamatus", "Taeromys_sp_katopasa", "Taeromys_tarae")
maxomys <- c("Crunomys_celebensis", "Maxomys_dollmani", "Maxomys_hellwaldii", "Maxomys_musschenbroekii", "Maxomys_wattsi")
margaretamys <- c("Margaretamys_elegans", "Margaretamys_parvus")
rattus <- c("Rattus_botanus", "Rattus_facetus", "Rattus_hoffmani", "Rattus_marmosurus", "Rattus_mollicomulus", "Rattus_xanthurus")
haeromys <- c("Haeromys_minahassae")

load(here("Species_Data", "Species_Extant.Rdata"))
```

# Cranium 


## Data and Function 
Function taken from Community Variance Function
```{r}
cran <- read_csv(here("Cranial_Data", "Cranial_36axes_Fitted.csv"))

get_cran <- function(sp, data, mountain) {
data %>% 
    filter(Species %in% {{sp}}) %>%
  #select(!Species) %>%
  select(!.row) %>%
  group_by(.draw) %>% 
  mutate(across(c(cPC1:cCsize), var, .names = "v{.col}")) %>%
    ungroup() %>% 
  mutate(cv_wei = rowSums(across(c(vcPC1:vcPC36)), na.rm = TRUE),
         cPC_wei = rowSums(across(c(cPC1:cPC36)), na.rm = TRUE)) %>% 
  select(.draw, vcCsize, cv_wei, Species, cPC_wei, cCsize) %>% 
    add_column(clade = {{mountain}})
}
```

## Cranium Shape Clade Variance

```{r}
c1 <- get_cran(echiothrix, cran, "Echiothrix")
c2 <- get_cran(bunomys, cran, "Bunomys") 
c3 <- get_cran(margaretamys, cran, "Margaretamys") 
c4 <- get_cran(maxomys, cran, "Maxomys")
c5 <- get_cran(rattus, cran, "Rattus")
c6 <- get_cran(haeromys,  cran, "Haeromys")
cct <- bind_rows(c1, c2, c3, c4, c5, c6)
write_csv(cct, here("Clade_Data", "Clade_Cranial_Variance_Weighted.csv"))

ords = c("Echiothrix", "Maxomys", "Bunomys", "Margaretamys", "Rattus", "Haeromys")
```


```{r}
p1 <- cct %>% 
ggplot(aes(y = factor(clade, levels = rev(ords)), x = cv_wei)) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  labs(x="Sum of Variance", y = "", fill = "Clade") +
  theme_classic() + theme(legend.position = "none",
                     panel.grid.major.y = element_line( size=.1, color="black" ))

p2 <- cct %>% ggplot(aes(y = factor(clade, levels = rev(ords)), x = cPC_wei, fill = Species)) +
  scale_fill_manual(values = c(rep("grey", 39))) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.2) +
  labs( y = "") +
  theme_classic() +
  theme(legend.position = "none",
        axis.text.y=element_blank(),
        panel.grid.major.y = element_line( size=.1, color="black" )) 

p1 + p2 + plot_layout(widths = c(1,2)) + plot_annotation(title = "Cranial Shape Disparity")
```

#Dentary

## Data and Function

```{r}
dent <- read_csv(here("Dentary_Data", "Dentary_20axes_Fitted.csv"))

get_dent <- function(sp, data, mountain) {
data %>% 
  filter(Species %in% {{sp}}) %>%
  #select(!Species) %>%
  select(!.row) %>%
  group_by(.draw) %>% 
  mutate(across(c(dPC1:dCsize), var, .names = "v{.col}")) %>%
    ungroup() %>% 
  mutate(dv_wei = rowSums(across(c(vdPC1:vdPC20)), na.rm = TRUE),
         dPC_wei = rowSums(across(c(dPC1:dPC20)), na.rm = TRUE)) %>% 
    select(.draw, vdCsize, dv_wei, dPC_wei, Species, dCsize) %>% 
    add_column(clade = {{mountain}})
}
```

## Dentary Shape Clade
```{r}
d1 <- get_dent(echiothrix,    dent, "Echiothrix")
d2 <- get_dent(bunomys,       dent, "Bunomys") 
d3 <- get_dent(margaretamys,  dent, "Margaretamys") 
d4 <- get_dent(maxomys,       dent, "Maxomys")
d5 <- get_dent(rattus,        dent, "Rattus")
d6 <- get_dent(haeromys,      dent, "Haeromys")
ddt <- bind_rows(d1, d2, d3, d4, d5, d6)
write_csv(ddt, here("Clade_Data", "Clade_Dentary_Variance_Weighted.csv"))
```

```{r}
p3 <- ddt %>% ggplot(aes(y = factor(clade, levels = rev(ords)), x = dv_wei)) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  labs(x="Sum of Variance", y = "", fill = "Clade") +
  theme_classic() + theme(legend.position = "none",
                     panel.grid.major.y = element_line( size=.1, color="black" ))

p4 <- ddt %>%  
  ggplot(aes(y = factor(clade, levels = rev(ords)), x = dPC_wei, fill = Species)) +
  scale_fill_manual(values = c(rep("grey", 39))) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.2) +
  labs( y = "") +
  theme_classic() +
  theme(legend.position = "none",
        axis.text.y=element_blank(),
        panel.grid.major.y = element_line( size=.1, color="black" ))  

p3 + p4 + plot_layout(widths = c(1,2)) + plot_annotation(title = "Dentary Shape Disparity")
```

# External Measurements

## Data and Function
```{r}
ext <- read_csv(here("External_Measurement_Data", "External_Fitted.csv"))

get_ext <- function(sp, data, mountain) {
data %>% 
  filter(Species %in% {{sp}}) %>%
  #select(!Species) %>%
  select(!.row) %>%
  group_by(.draw) %>%  
  mutate(vHB = var(HB),
            vTail = var(rTail),
            vHF = var(rHF),
            vEar = var(rEar),
            vMass = var(lMass)) %>% 
  mutate(ext_sum = vHB + vTail + vHF + vEar + vMass) %>% 
  mutate(ext_scaled = ext_sum/5) %>% 
  add_column(clade = {{mountain}})
}

```
## External Clade
```{r}
c1 <- get_ext(echiothrix,    ext, "Echiothrix")
c2 <- get_ext(bunomys,       ext, "Bunomys") 
c3 <- get_ext(margaretamys,  ext, "Margaretamys") 
c4 <- get_ext(maxomys,       ext, "Maxomys")
c5 <- get_ext(rattus,        ext, "Rattus")
c6 <- get_ext(haeromys,      ext, "Haeromys")
eet <- bind_rows(c1, c2, c3, c4, c5, c6)
write_csv(eet, here("Clade_Data", "Clade_External_Variance_Fitted.csv"))
```

```{r}
p5 <- eet %>% ggplot(aes(y = factor(clade, levels = rev(ords)), x = vTail)) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  labs(x="Sum of Variance", y = "", fill = "Clade") +
  theme_classic() + theme(legend.position = "none",
                     panel.grid.major.y = element_line( size=.1, color="black" ))

p6 <- eet %>% 
  ggplot(aes(y = factor(clade, levels = rev(ords)), x = rTail, fill = Species)) +
  scale_fill_manual(values = c(rep("grey", 39))) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.2) +
  labs( y = "") +
  theme_classic() +
  theme(legend.position = "none",
        axis.text.y=element_blank(),
        panel.grid.major.y = element_line( size=.1, color="black" )) 

p5 + p6 + plot_layout(widths = c(1,2)) + plot_annotation(title = "Tail Disparity")
```

```{r}
p7 <- eet %>% ggplot(aes(y = factor(clade, levels = rev(ords)), x = vHB)) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  labs(x="Sum of Variance", y = "", fill = "Clade") +
  theme_classic() + theme(legend.position = "none",
                     panel.grid.major.y = element_line( size=.1, color="black" ))

p8 <- eet %>% 
  ggplot(aes(y = factor(clade, levels = rev(ords)), x = HB, fill = Species)) +
  scale_fill_manual(values = c(rep("grey", 39))) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.2) +
  labs( y = "") +
  theme_classic() +
  theme(legend.position = "none",
        axis.text.y=element_blank(),
        panel.grid.major.y = element_line( size=.1, color="black" )) 

p7 + p8 + plot_layout(widths = c(1,2)) + plot_annotation(title = "Head-Body Length Disparity")
```

```{r}
p9 <- eet %>% ggplot(aes(y = factor(clade, levels = rev(ords)), x = vHF)) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  labs(x="Sum of Variance", y = "", fill = "Clade") +
  theme_classic() + theme(legend.position = "none",
                     panel.grid.major.y = element_line( size=.1, color="black" ))

p10 <- eet %>% 
  ggplot(aes(y = factor(clade, levels = rev(ords)), x = rHF, fill = Species)) +
  scale_fill_manual(values = c(rep("grey", 39))) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.2) +
  labs( y = "") +
  theme_classic() +
  theme(legend.position = "none",
        axis.text.y=element_blank(),
        panel.grid.major.y = element_line( size=.1, color="black" )) 

p9 + p10 + plot_layout(widths = c(1,2)) + plot_annotation(title = "Hind Foot Length Disparity")
```


# Isotopes

## Data and Function

```{r}
iso <- read_csv(here("Isotope_Data", "Isotope_Group_Level_Fitted.csv"))

get_iso <- function(sp, data, mountain) {
data %>% 
  filter(Species %in% {{sp}}) %>%
  #select(!Species) %>%
  select(!.row) %>%
  group_by(.draw) %>%  
  mutate(vN15 = var(sN15),
        vC13 = var(sC13),
        vIso = (vN15 + vC13)/2,
        Iso = (sN15 + sC13)/2) %>% 
  add_column(clade = {{mountain}})
}
```

# Iso Clade Variance
```{r}
c1 <- get_iso(echiothrix,    iso, "Echiothrix")
c2 <- get_iso(bunomys,       iso, "Bunomys") 
c3 <- get_iso(margaretamys,  iso, "Margaretamys") 
c4 <- get_iso(maxomys,       iso, "Maxomys")
c5 <- get_iso(rattus,        iso, "Rattus")
c6 <- get_iso(haeromys,      iso, "Haeromys")
ist <- bind_rows(c1, c2, c3, c4, c5, c6)
write_csv(ist, here("Clade_Data", "Clade_Isotope_Fitted.csv"))
```


```{r}
p11 <- ist %>% ggplot(aes(y = factor(clade, levels = rev(ords)), x = vN15)) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  labs(x="Sum of Variance", y = "", fill = "Clade") +
  theme_classic() + theme(legend.position = "none",
                     panel.grid.major.y = element_line( size=.1, color="black" ))

p12 <- ist %>% 
  ggplot(aes(y = factor(clade, levels = rev(ords)), x = sN15, fill = Species)) +
  scale_fill_manual(values = c(rep("grey", 39))) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.2) +
  labs( y = "") +
  theme_classic() +
  theme(legend.position = "none",
        axis.text.y=element_blank(),
        panel.grid.major.y = element_line( size=.1, color="black" )) 

#pp1 <- 
p11 + p12 + plot_layout(widths = c(1,2)) + plot_annotation(title = "N15 Disparity")
```




#Combine and Save
```{r}
dat <- cct %>% right_join(ddt) %>% right_join(eet) %>% right_join(ist)
dat %>% write_csv(here("Clade_Data", "Clade_Varaince.csv"))
rm(cct, ddt, ext, ist)
```

# Locomotor Variance
## Data and Function
```{r}
loc <- read_csv(here("Locomotion_Data", "Locomotion_List.csv"))

get_loc<- function(sp, data, mountain) {
data %>% 
  filter(Species %in% {{sp}}) %>%
  #select(!Species) %>%
  #select(!.row) %>%
 # group_by(.draw) %>%  
  mutate(vloc = var(Loc)) %>% 
  add_column(clade = {{mountain}})
}
```
## Loc Var
```{r}
c1 <- get_loc(echiothrix,    loc, "Echiothrix")
c2 <- get_loc(bunomys,       loc, "Bunomys") 
c3 <- get_loc(margaretamys,  loc, "Margaretamys") 
c4 <- get_loc(maxomys,       loc, "Maxomys")
c5 <- get_loc(rattus,        loc, "Rattus")
c6 <- get_loc(haeromys,      loc, "Haeromys")
lst <- bind_rows(c1, c2, c3, c4, c5, c6)
write_csv(lst, here("Clade_Data", "Clade_Locomotion_Var.csv"))
```



#Plotting the Clade Fitted Varaince

```{r}
pacman::p_load(tidyverse, patchwork, tidybayes)
dat <- read_csv(here("Clade_Data", "Clade_Varaince.csv"))
ldat <- read_csv(here("Locomotion_Data", "Clade_Locomotion_Var.csv"))
```

## Plotting Functions



```{r}
vplot <- function(var, xlab){
dat %>% 
    ggplot(aes(y = factor(clade, levels = rev(ords)), x = {{var}})) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  labs(x={xlab}, y = "") +
  theme_classic() + theme(legend.position = "none",
                     panel.grid.major.y = element_line( size=.1, color="black" ))
}

splot <- function(var, xlab){
  dat %>% 
    ggplot(aes(y = factor(clade, levels = rev(ords)), x = {{var}}, fill = Species)) +
    scale_fill_manual(values = c(rep("grey", 39))) +
    stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.2) +
    labs( x = {xlab}, y = "") +
    theme_classic() +
    theme(legend.position = "none",
          axis.text.y=element_blank(),
          panel.grid.major.y = element_line( size=.1, color="black" )) 
}
```



```{r}
p1 <-  vplot(cv_wei, "Cranial Shape Var.")
p2 <-  vplot(vcCsize, "Cranial Size Var.")
p3 <-  vplot(dv_wei, "Dentary Shape Var.")
p4 <-  vplot(vdCsize, "Dentary Size Var.")
p5 <-  vplot(vN15, "15N Var.")
p6 <-  vplot(vC13, "13C Var.")
p7 <-  vplot(vHB, "Head-Body Length Var.")
p8 <-  vplot(vMass, "log(Mass) Var.")
p9 <-  vplot(vTail, "Tail Length Var")
p10 <-  vplot(vHF, "Hind Foot Length Var.")
p11 <-  vplot(vEar, "Ear Length Var.")


vplot(vN15, "15N Var.")
vplot(vC13, "13C Var.")


s1 <-  splot(cPC_wei, "Cranial Shape")
s2 <-  splot(cCsize, "Cranial Size")
s3 <-  splot(dPC_wei, "Dentary Shape")
s4 <-  splot(dCsize, "Dentary Size.")
s5 <-  splot(sN15, "15N")
s6 <-  splot(sC13, "13C")
s7 <-  splot(HB, "Head-Body Length")
s8 <-  splot(lMass, "log(Mass)")
s9 <-  splot(rTail, "Tail Length")
s10 <-  splot(rHF, "Hind Foot Length")
s11 <-  splot(rEar, "Ear Length")
```
# Locomotor Var
```{r}
p12 <- lst %>% select(vloc, clade) %>% 
  ggplot(aes(y = factor(clade, levels = rev(ords)), x = vloc)) +
  geom_point(shape = 15, size = 10,
             position = position_nudge(y = .28), color = "grey30") +
  geom_point(shape = 15, size = 10,
             position = position_nudge(y = .5), color = "grey30") +
  scale_y_discrete(drop = F) +
  scale_x_continuous(breaks = c(0, 0.2, 0.4, 0.6), limits = c(-.01, 0.61)) +
  labs(x="Locomotor Var.", y = "") +
  theme_classic() + 
  theme(legend.position = "none",
        panel.grid.major.y = element_line( size=.1, color="black" ))
p12

```

```{r}
s12 <- lst %>% 
  mutate(clade = as.factor(clade),
         mlt = rep(c(-0.13,0, 0.13), length.out = 39),
         Loc = as.numeric(Loc),
         Loc2 = Loc+mlt) %>% 
    ggplot(aes(x = factor(clade, levels = rev(ords)), y = Loc2)) + 
  geom_dotplot(binaxis='y', 
               position = "dodge", 
               binwidth = 0.13, 
               colour = "grey30",
               fill = "grey30") + 
  scale_y_continuous(labels= c('Arboreal',
                               'General', 
                               'Terrestrial',
                               'Amphibious'), 
                     breaks=1:4) +
  coord_flip() +
  labs( y = 'Locomotor Mode', x = "") +
  theme_classic() + 
  theme(axis.text.y=element_blank(),
        axis.text.x = element_text(size = 6.5),
        panel.grid.major.y = element_line( size=.1, color="black" ))


s12

```

# Big Plot
```{r warning=FALSE}
layout <- "
ABBCDD
EFFGHH
IJJKLL
MNNOPP
QRRSTT
UVVWXX
"

p1 + s1 + p2 + s2 + p3 + s3 + p4 + s4 + p5 +s5 + p6 + s6 + p7 + s7 + p8 + s8 + p9 + s9 + p10 + s10 + p11 + s11 + p12 + s12 +
  plot_layout(design = layout, tag_level = 'new') + plot_annotation(tag_levels = list(c('A', '', 'B', '', 'C', '', 'D', '', 'E', '', 'F', '', 'G', '', 'H', '', 'I', '', 'J', '', 'K', '', 'L', '')))

ggsave(here("Plots", "FigS5_Clade_Var.pdf"), height = 23.25, width =12)

```


# Differences & HeatMap

```{r}
library(pals)

p1 <- dat %>% select(2:3, 7:9, 17:22, 26:28) %>% 
  filter(clade != "Haeromys") %>% 
  group_by(clade) %>% 
  summarise(across(everything(), ~ mean(.x, na.rm = TRUE))) %>% 
  #group_by(clade) %>%
  mutate(across(c(2:14), ~scales::rescale(.x))) %>% 
   pivot_longer(!clade, names_to = "trait", values_to = "value") %>% 
  ggplot(aes(x=trait, y=clade, fill= value)) + 
  geom_tile() +
  scale_fill_gradientn(colours=rev(cubicyf(100)), guide = "colourbar") +
  theme(axis.text.x = element_text(angle = -50, vjust = 1, hjust = 0, size = 8)) +
  coord_fixed() + theme_classic()

p2 <- dat %>% select(2:3, 7:9, 17:22, 26:28) %>% 
  filter(clade != "Haeromys") %>%  
  group_by(clade) %>% 
  summarise(across(everything(), ~ mean(.x, na.rm = TRUE))) %>% 
  #group_by(clade) %>%
  mutate(across(c(2:14), ~scales::rescale(.x))) %>% 
   pivot_longer(!clade, names_to = "trait", values_to = "value") %>% 
  filter(!clade %in% c("Haeromys", "Margaretamys", "Rattus")) %>%
  ggplot(aes(x=trait, y=clade, fill= value)) + 
  geom_tile() +
  scale_fill_gradientn(colours=rev(cubicyf(100)), guide = "colourbar") +
  theme(axis.text.x = element_text(angle = -50, vjust = 1, hjust = 0, size = 8)) +
  coord_fixed() + theme_classic()

p1 / p2
```

```{r warning=FALSE}
dat_long <- dat %>% select(2:3, 7:9, 17:22, 26:28) %>% 
    filter(clade != "Haeromys") %>% 
    group_by(clade) %>% 
    summarise(across(everything(), ~ mean(.x, na.rm = TRUE))) %>% 
    mutate(across(c(2:14), ~scales::rescale(.x))) %>% 
    ungroup() %>% 
    t() %>% as.data.frame() %>%  tibble::rownames_to_column() %>%
  janitor::row_to_names(row_number = 1) %>% 
  rename(trait = clade) %>%
  mutate(rn = row_number()) %>%
    pivot_longer(!c(trait,rn), names_to = "clade", values_to = "value") 

dat_long %>% 
  full_join(dat_long, by = c( "trait","rn")) %>%
  filter(clade.x != clade.y) %>%
  distinct(trait, rn, 
           combo_name = paste0(pmin(clade.x, clade.y), pmax(clade.x, clade.y)),
           .keep_all = TRUE) %>% 
  mutate(diff = as.numeric(value.x) - as.numeric(value.y),
         abs_diff = abs(diff)) %>%
  select(trait, combo_name, abs_diff) %>% 
  ggplot(aes(x = abs_diff, y = trait, color = combo_name)) + geom_point(size = 4, alpha = 0.7) +
  theme_bw()
```

