---
title: "Density Estimates"
---

# Estmate Density Using Mean Nearest Neighbor

This script estimates the density of traits in the communities using the Mean Nearest Neighbor metric. There are some differences in these estimates when compared to the sum of variance estimates. The biggest difference is that, when estimating the density for all traits, nearest neighbor doesn't work with species missing from some values. Therefore we need to create a separate species list for each community that does not include the missing species. This will be at the bottom of the script. 

Load packages and data and functions
Most of these are different species lists.
```{r}
pacman::p_load(here, tidyverse, tidybayes, modelr, furrr, dispRity, patchwork)

here::i_am('Code/Models_Fitted_Variance.Rmd')

#List of species by community
load(here("Species_Data", "Species_Lists.Rdata"))
#List of all species
load(here("Species_Data", "Species_Extant.RData"))

scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = na.rm)) / sd(x, na.rm)
level_order <-  c( 'Bawakaraeng', 'Buliohuto','Dako', "Katopasa", "Ambang", "Latimojong", "Torompupu", "Nokilalaki", "Gandangdewata")
level_order_iso <-  c( 'Bawakaraeng', 'Buliohuto','Dako',  "Ambang", "Latimojong",  "Gandangdewata")

adat <- read_csv(here("All_Traits.csv"))
```

These scripts use the package `furrr` which is a multi-threading version of `purrr`. It incorperates the `futures` package to run on as many cores as you choose. Here I am selecting 6 cores on my laptop.
```{r}
furrr_options(seed = TRUE)
options(future.rng.onMisuse="ignore")
options(readr.show_col_types = FALSE)
plan(multisession, workers = 6)
```

## Functions   

#### Nearest Neighbor Function  

This function gets a mean nearest neighbor value for each Bayesian draw of the trait estimate. So 1000 draws (what I am using) yields 1000 Mean Nearest Neighbor values.

 Neighbours function that allows NA's
 Edited from https://github.com/TGuillerme/dispRity/blob/61baa826cc965db22c319f4d6e2ffb3550da682d/R/sanitizing.R and https://github.com/TGuillerme/dispRity/blob/f249475f4f7b3f2bd2af00e36a435dacaafaf200/R/dispRity.metric.R
```{r}
neighbours2 <- function(matrix, which = min, method = "euclidean") {
    ## Check if the matrix is a distance matrix first
    distances <- as.matrix(check.dist.matrix2(matrix, method = method)[[1]])
    ## Remove the diagonals
    diag(distances) <- NA
    ## Get the selected distances for each rows
    return(unname(apply(distances, 1, which, na.rm = TRUE)))
}

check.dist.matrix2 <- function(matrix, method, just.check = FALSE, ...) {

    ## Is distance
    was_dist <- FALSE

    ## Check if distance
    if(is(matrix, "dist")) {
        return(list(matrix, "was_dist" = TRUE))
    }

    ## Is the matrix square?
    if(dim(matrix)[1] == dim(matrix)[2] &&
       all(diag(as.matrix(matrix)) == 0) &&
       all(matrix[upper.tri(matrix)] == matrix[rev(lower.tri(matrix))])) {
        ## It was a distance matrix!
        was_dist <- TRUE
    }

    if(just.check) {
        ## Simply return the check
        return(was_dist)
    } else {
        ## Return a matrix
        if(was_dist) {
            return(list(stats::as.dist(matrix), "was_dist" = TRUE))
        } else {
            return(list(vegan::vegdist(matrix, method = method, na.rm = TRUE, ...), "was_dist" = FALSE))
        }
    }
}

```

#### Nearest Neighbor Function2
This function runs the previous NN function on all dataframes. 
```{r}
get_mnni <- function(data, sp) {
  data %>% 
    filter(Species %in% {{sp}}) %>% 
  #Split dataframe by draws into 1000 data frames
  split(.$.draw) %>% 
  #and then drop the .draw column that defines the groups - FASTER VERSION
  map(., ~ .x[ ,-c(1:2)])  %>% 
  # Run the functions......
  map(~ .x %>%
        ### Run the Mean Nearest Neighbor Function (From dispRity)
        neighbours2() %>%
        # then get the mean
        mean()
        ) %>% 
  unlist() %>% 
  as_tibble() 
  }
```

## Cranial Nearest Neighbor

```{r}
cdat <- read_csv(here("Cranial_Data", "Cranial_36axes_Fitted.csv"))
```

### NN Estimate 
```{r}
cf <- cdat %>% 
  select(c(Species, .draw, cPC1:cPC36)) 

amb_nni <- get_mnni(cf, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(cf, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(cf, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(cf, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(cf, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(cf, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(cf, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(cf, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(cf, sptor) %>%  mutate(com = "Torompupu" )

nn_cran2 <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(c_nn36 = value)
```

#### Write to `All_Traits`  
```{r}
dd <- nn_cran2 %>% select(c_nn36)
adat <- read_csv(here("All_Traits.csv"))
adat <- adat  %>% bind_cols(dd)
adat %>% write_csv(here("All_Traits.csv"))
```

#### Cranium Plot
test plot
```{r}
myx <- "Mean Nearest Neighbor Distance"
nn_cran2 %>% 
  mutate(com = factor(com, level = level_order)) %>% 
  ggplot(aes(y = factor(com, level = level_order), x =c_nn36, fill = com)) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  labs(title="PC's 1-36", y = "", fill = "Mountain") +
  theme_bw() +
  guides(fill = guide_legend(reverse=T)) + 
  theme(legend.position = "none") 
```


### Cranial Size Estimate  

```{r}
cf <- cdat %>% 
  select(c(Species, .draw, cCsize)) 

amb_nni <- get_mnni(cf, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(cf, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(cf, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(cf, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(cf, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(cf, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(cf, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(cf, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(cf, sptor) %>%  mutate(com = "Torompupu" )


nn_csize <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(csize_nn = value)
```

#### Write to `All_Traits`
```{r}
dd <- nn_csize %>% select(csize_nn)
adat <- adat  %>% bind_cols(dd)

```

## Dentary Nearest Neighbor

```{r}
ddat <- read_csv(here("Dentary_Data", "Dentary_20axes_Fitted.csv"))
```


### NN Estimate  

```{r}
df <- ddat %>% 
  select(c(Species, .draw, dPC1:dPC20)) 

amb_nni <- get_mnni(df, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(df, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(df, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(df, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(df, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(df, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(df, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(df, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(df, sptor) %>%  mutate(com = "Torompupu" )

myx <- "Mean Nearest Neighbor Distance"

nn_dent <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(d_nn20 = value)
```

#### Dentary Plot
test plot
```{r}
nn_dent %>% 
  mutate(com = factor(com, level = level_order)) %>%  
  ggplot(aes(y = factor(com, level = level_order), x =d_nn20, fill = com)) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
  labs(title="PC's 1-20", y = "", fill = "Mountain") +
  xlab(bquote(.(myx))) +
  theme_bw() +
  guides(fill = guide_legend(reverse=T)) + 
  theme(legend.position = "none") 
```


#### Write to `All_Traits`
```{r}
dd <- nn_dent2 %>% select(d_nn20)
adat <- read_csv(here("All_Traits.csv"))
adat <- adat  %>% bind_cols(dd)
adat %>% write_csv(here("All_Traits.csv"))
```

Very similar to cranial!

### Dentary Size Estimate
```{r}
df <- ddat %>% 
  select(c(Species, .draw, dCsize)) 

amb_nni <- get_mnni(df, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(df, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(df, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(df, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(df, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(df, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(df, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(df, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(df, sptor) %>%  mutate(com = "Torompupu" )

nn_dsize <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(dsize_nn = value)
```

#### Write to `All_Traits`
```{r}

dd <- nn_dsize %>% select(dsize_nn)
adat <- adat  %>% bind_cols(dd)
```


## Skull Nearest Neighbor 

```{r}
skdat <- ddat  %>% select(!.row) %>% 
  full_join(cdat, by = c(".draw", "Species"))
```


### Skull NN Estimate
```{r}
df <- skdat %>% 
  select(c(Species, .draw, dPC1:dPC20, cPC1:cPC36)) 

amb_nni <- get_mnni(df, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(df, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(df, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(df, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(df, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(df, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(df, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(df, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(df, sptor) %>%  mutate(com = "Torompupu" )

nn_sk2 <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(sk_nn56 = value)

rm(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni)
```

#### Write to `All_Traits`
```{r}
dd <- nn_sk2 %>% select(sk_nn56)
adat <- adat %>% bind_cols(dd)
```



## External Measurements

```{r}
edat <- read_csv(here("External_Measurement_Data", "External_Fitted.csv"))
```

### Head-Body NN
```{r}
df <- edat %>% 
  select(c(Species, .draw, HB)) 

amb_nni <- get_mnni(df, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(df, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(df, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(df, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(df, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(df, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(df, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(df, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(df, sptor) %>%  mutate(com = "Torompupu" )

nn_HB <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(HB_nn = value)
```

#### Write  
```{r}
dd <- nn_HB %>% select(HB_nn)
adat <- adat %>% bind_cols(dd)
```

### Tail NN
```{r}
df <- edat %>% 
  select(c(Species, .draw, rTail)) 

amb_nni <- get_mnni(df, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(df, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(df, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(df, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(df, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(df, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(df, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(df, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(df, sptor) %>%  mutate(com = "Torompupu" )

nn_Tail <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(Tail_nn = value)
```

#### Write  
```{r}
dd <- nn_Tail %>% select(Tail_nn)
adat <- adat %>% bind_cols(dd)
```

### HF NN
```{r}
df <- edat %>% 
  select(c(Species, .draw, rHF)) 

amb_nni <- get_mnni(df, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(df, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(df, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(df, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(df, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(df, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(df, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(df, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(df, sptor) %>%  mutate(com = "Torompupu" )

nn_HF <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(HF_nn = value)
```

#### write
```{r}
dd <- nn_HF %>% select(HF_nn)
adat <- adat %>% bind_cols(dd)
```


### Ear NN
```{r}
df <- edat %>% 
  select(c(Species, .draw, rEar)) 

amb_nni <- get_mnni(df, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(df, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(df, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(df, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(df, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(df, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(df, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(df, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(df, sptor) %>%  mutate(com = "Torompupu" )

nn_Ear <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(Ear_nn = value)
```

#### write
```{r}
dd <- nn_Ear %>% select(Ear_nn)
adat <- adat %>% bind_cols(dd)
```

### Mass NN
```{r}
df <- edat %>% 
  select(c(Species, .draw, lMass)) 

amb_nni <- get_mnni(df, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(df, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(df, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(df, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(df, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(df, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(df, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(df, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(df, sptor) %>%  mutate(com = "Torompupu" )

nn_Mass <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(Mass_nn = value)
```

#### write
```{r}
dd <- nn_Mass %>% select(Mass_nn)
adat <- adat %>% bind_cols(dd)
```


### Body size NN
```{r}
df <- edat %>% 
  select(c(Species, .draw, lMass, HB)) 

amb_nni <- get_mnni(df, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(df, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(df, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(df, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(df, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(df, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(df, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(df, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(df, sptor) %>%  mutate(com = "Torompupu" )

nn_Bsz <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(Bsz_nn = value)
```

#### write
```{r}
dd <- nn_Bsz %>% select(Bsz_nn)
adat <- adat %>% bind_cols(dd)
```

### All External NN

```{r}
df <- edat %>% 
  select(c(Species, .draw, HB, rTail, rHF, rEar, lMass)) 

amb_nni <- get_mnni(df, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(df, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(df, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(df, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(df, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(df, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(df, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(df, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(df, sptor) %>%  mutate(com = "Torompupu" )

nn_ext <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(ext_nn = value)
```

#### Write
```{r}
dd <- nn_ext %>% select(ext_nn)
adat <- adat %>% bind_cols(dd)
```

### Morpho NN
This is skull shape and external measurements hb, tail, hf, lmass, ear

```{r}
morph_dat <-  skdat  %>% select(!.row) %>% select(Species, .draw, dPC1, dPC2, dPC3, cPC1, cPC2) %>% 
  full_join(edat, by = c(".draw", "Species"))


df <- morph_dat %>% 
  select(!.row) 

amb_nni <- get_mnni(df, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(df, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(df, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(df, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(df, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(df, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(df, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(df, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(df, sptor) %>%  mutate(com = "Torompupu" )

nn_morph <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(morpho_nn = value)
```

#### write
```{r}
dd <- nn_morph %>% select(morpho_nn)
adat <- adat %>% bind_cols(dd)


rm(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni)
```


```{r}
adat %>% write_csv(here("All_Traits.csv"))
```

## Isotope GROUP Nearest Neighbor

Realized I have to use the grouping data again. Thats ok. It'll be just like any of the other variables.
### N15 Group NN
```{r}
idat <- read_csv(here("Isotope_Data", "Isotope_Group_Level_Fitted.csv")) %>% select(Species, .draw, sN15)


amb_nni <- get_mnni(idat, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(idat, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(idat, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(idat, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(idat, spgan) %>%  mutate(com = "Gandangdewata" )
#kat_nni <- get_mnni(idat, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(idat, splat) %>%  mutate(com = "Latimojong" )
#nok_nni <- get_mnni(idat, spnok) %>%  mutate(com = "Nokilalaki" )
#tor_nni <- get_mnni(idat, sptor) %>%  mutate(com = "Torompupu" )


nn_N <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, lat_nni) %>% rename(N15_nn = value) %>% mutate(.draw = rep(1:4000, 6))
```

#### write
```{r}
adat <- adat  %>% 
  full_join(nn_N, by = c(".draw", "com"))
```

### C13 Group NN
```{r}
idat <- read_csv(here("Isotope_Data", "Isotope_Group_Level_Fitted.csv")) %>% select(Species, .draw, sC13)


amb_nni <- get_mnni(idat, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(idat, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(idat, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(idat, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(idat, spgan) %>%  mutate(com = "Gandangdewata" )
#kat_nni <- get_mnni(idat, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(idat, splat) %>%  mutate(com = "Latimojong" )
#nok_nni <- get_mnni(idat, spnok) %>%  mutate(com = "Nokilalaki" )
#tor_nni <- get_mnni(idat, sptor) %>%  mutate(com = "Torompupu" )


nn_C <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, lat_nni) %>% rename(C13_nn = value) %>% mutate(.draw = rep(1:4000, 6))
```

#### Write
```{r}
adat <- adat  %>% 
  full_join(nn_C, by = c(".draw", "com"))
```

### Iso Group NN
```{r}
idat <- read_csv(here("Isotope_Data", "Isotope_Group_Level_Fitted.csv")) %>% select(Species, .draw, sC13, sN15)


amb_nni <- get_mnni(idat, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(idat, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(idat, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(idat, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(idat, spgan) %>%  mutate(com = "Gandangdewata" )
#kat_nni <- get_mnni(idat, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(idat, splat) %>%  mutate(com = "Latimojong" )
#nok_nni <- get_mnni(idat, spnok) %>%  mutate(com = "Nokilalaki" )
#tor_nni <- get_mnni(idat, sptor) %>%  mutate(com = "Torompupu" )


nn_i <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, lat_nni) %>% rename(iso_nn = value) %>% mutate(.draw = rep(1:4000, 6))
```

#### write
```{r}
adat <- adat  %>% 
  full_join(nn_i, by = c(".draw", "com"))
```

## Write Data to File
```{r}
adat %>% write_csv(here("All_Traits.csv"))
```
