---
title: "Density Estimates"
---

# Estmate Density Using Mean Nearest Neighbor

This script estimates the density of traits in the communities using the Mean Nearest Neighbor metric. There are some differences in these estimates when compared to the sum of variance estimates. The biggest difference is that, when estimating the density for all traits, nearest neighbor doesn't work with species missing from some values. Therefore we need to create a separate species list for each community that does not include the missing species. This will be at the bottom of the script. 

Load packages and data and functions
Most of these are different species lists.
```{r}
pacman::p_load(here, tidyverse, tidybayes, brms, modelr, furrr, dispRity, patchwork)

here::i_am('Code/Models_Fitted_Variance.Rmd')

#List of species by community
load(here("Species_Data", "Species_Lists.Rdata"))
#List of all species
load(here("Species_Data", "Species_Extant.RData"))

scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = na.rm)) / sd(x, na.rm)
level_order <-  c( 'Bawakaraeng', 'Buliohuto','Dako', "Katopasa", "Ambang", "Latimojong", "Torompupu", "Nokilalaki", "Gandangdewata")
level_order_iso <-  c( 'Bawakaraeng', 'Buliohuto','Dako',  "Ambang", "Latimojong",  "Gandangdewata")

adat <- read_csv(here("All_Traits.csv"))
```

These scripts use the package `furrr` which is a multi-threading version of `purrr`. It incorperates the `futures` package to run on as many cores as you choose. Here I am selecting 6 cores on my laptop.
```{r}
furrr_options(seed = TRUE)
options(future.rng.onMisuse="ignore")
options(readr.show_col_types = FALSE)
plan(multisession, workers = 6)
```

#### Nearest Neighbor Function
This function gets a mean nearest neighbor value for each Bayesian draw of the trait estimate. So 1000 draws (what I am using) yields 1000 Mean Nearest Neighbor values.

 Neighbours function that allows NA's
 Edited from https://github.com/TGuillerme/dispRity/blob/61baa826cc965db22c319f4d6e2ffb3550da682d/R/sanitizing.R and https://github.com/TGuillerme/dispRity/blob/f249475f4f7b3f2bd2af00e36a435dacaafaf200/R/dispRity.metric.R
```{r}
neighbours2 <- function(matrix, which = min, method = "euclidean") {
    ## Check if the matrix is a distance matrix first
    distances <- as.matrix(check.dist.matrix2(matrix, method = method)[[1]])
    ## Remove the diagonals
    diag(distances) <- NA
    ## Get the selected distances for each rows
    return(unname(apply(distances, 1, which, na.rm = TRUE)))
}

check.dist.matrix2 <- function(matrix, method, just.check = FALSE, ...) {

    ## Is distance
    was_dist <- FALSE

    ## Check if distance
    if(is(matrix, "dist")) {
        return(list(matrix, "was_dist" = TRUE))
    }

    ## Is the matrix square?
    if(dim(matrix)[1] == dim(matrix)[2] &&
       all(diag(as.matrix(matrix)) == 0) &&
       all(matrix[upper.tri(matrix)] == matrix[rev(lower.tri(matrix))])) {
        ## It was a distance matrix!
        was_dist <- TRUE
    }

    if(just.check) {
        ## Simply return the check
        return(was_dist)
    } else {
        ## Return a matrix
        if(was_dist) {
            return(list(stats::as.dist(matrix), "was_dist" = TRUE))
        } else {
            return(list(vegan::vegdist(matrix, method = method, na.rm = TRUE, ...), "was_dist" = FALSE))
        }
    }
}

```


```{r}
get_mnni <- function(data, sp) {
  data %>% 
    filter(Species %in% {{sp}}) %>% 
  #Split dataframe by draws into 1000 data frames
  split(.$.draw) %>% 
  #and then drop the .draw column that defines the groups - FASTER VERSION
  map(., ~ .x[ ,-c(1:2)])  %>% 
  # Run the functions......
  map(~ .x %>%
        ### Run the Mean Nearest Neighbor Function (From dispRity)
        neighbours2() %>%
        # then get the mean
        mean()
        ) %>% 
  unlist() %>% 
  as_tibble() 
  }
```

# Cranial Nearest Neighbor
Load the necessary data

```{r}
cdat <- read_csv(here("Cranial_Data", "Cranial_36axes_Fitted.csv"))
```
#### Broken Stick

Nearest neighbor requires all the axes to be treated the same (unlike what we did in the sum of variance method). Because of this, it isn't a good idea to use ALL or nearly ALL of the axes, as the nearest neighbor on axis 17 isn't nearly as biologically meaningful as the nearest neighbor on axis 1 or 2. So we need to do some PC selection. Using the broken stick method from `PCDimension` package:

```{r}
a = rep(1:36)
#these are the PC variance values for the cranial Procrusted PCA
true = c(0.204147859, 0.147885771, 0.064424297, 0.060399156, 0.043421343, 0.038126757, 0.036660724, 0.033351233, 0.030241809, 0.027281399, 0.023312389, 0.020690302, 0.017886499, 0.016987085, 0.016170664, 0.015161306, 0.014232396, 0.01234345, 0.011657948, 0.0105006, 0.009831498, 0.009525746, 0.009019535, 0.008004607, 0.007836483, 0.007517283, 0.007160749, 0.006919011, 0.00631384, 0.005867241, 0.005440684, 0.005212542, 0.005101055, 0.004628909, 0.004261733, 0.003790978)
expected = PCDimension::brokenStick(1:36, 36)
c_bs = data.frame(a, true, expected)
c_bs
```
Looking at this, the %variation falls below the expected variation on the 3rd PC

#### Cranial NN Estimate
Estimate Cranial Shape Nearest Neighbor for each community
```{r}
cf <- cdat %>% 
  select(c(Species, .draw, cPC1, cPC2)) 

amb_nni <- get_mnni(cf, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(cf, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(cf, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(cf, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(cf, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(cf, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(cf, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(cf, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(cf, sptor) %>%  mutate(com = "Torompupu" )

nn_cran <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(c_nn = value)
```

```{r}
dd <- nn_cran %>% select(c_nn)
adat <- adat  %>% bind_cols(dd)
```

test plot
```{r}
myx <- "Mean Nearest Neighbor Distance"
nn_cran %>% 
  mutate(com = factor(com, level = level_order)) %>% 
 ggplot(aes(y = factor(com, level = level_order), x =c_nn, fill = com)) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
   labs(title="Broken Stick: PC's 1&2", y = "", fill = "Mountain") +
  xlab(bquote(.(myx)^-1)) +
  #xlim(1, 3.2) + 
  theme_bw() + scale_fill_viridis_d(direction = -1, begin = 0, end = 0.9, option = "A") + guides(fill = guide_legend(reverse=T)) + theme(legend.position = "none") 
```

# Cranial NN - No Scale
The previous way I did this was a work around for dealing with the variance of each PC axis, but turns out that that was only a problem because I was SCALING the data. The natural cumulative variance of each PC axis is intrinsic in the values themselves, so in theory I could do NN analyses without using broken stick.

Lets try that. Going to copy and edit the code above. 

```{r}
cdat <- read_csv(here("Cranial_Data", "Cranial_36axes_Fitted.csv"))
```

#### NN Estimate
```{r}
cf <- cdat %>% 
  select(c(Species, .draw, cPC1:cPC36)) 

amb_nni <- get_mnni(cf, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(cf, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(cf, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(cf, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(cf, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(cf, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(cf, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(cf, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(cf, sptor) %>%  mutate(com = "Torompupu" )

nn_cran2 <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(c_nn = value)
```

```{r}
#dd <- nn_cran %>% select(c_nn)
#adat <- adat  %>% bind_cols(dd)
```

#### Quick Plot
```{r}
myx <- "Mean Nearest Neighbor Distance"
p1 <- nn_cran %>% 
  mutate(com = factor(com, level = level_order)) %>% 
 ggplot(aes(y = factor(com, level = level_order), x =c_nn, fill = com)) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
   labs(title="Broken Stick:PCs 1-2", y = "", fill = "Mountain") +
  xlab(bquote(.(myx)^-1)) +
  #xlim(1, 3.2) + 
  theme_bw() + scale_fill_viridis_d(direction = -1, begin = 0, end = 0.9, option = "A") + guides(fill = guide_legend(reverse=T)) + theme(legend.position = "none") 
p2 <- nn_cran2 %>% 
  mutate(com = factor(com, level = level_order)) %>% 
 ggplot(aes(y = factor(com, level = level_order), x =c_nn, fill = com)) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
   labs(title="PCs 1-36", y = "", fill = "Mountain") +
  xlab(bquote(.(myx)^-1)) +
  #xlim(1, 3.2) + 
  theme_bw() + scale_fill_viridis_d(direction = -1, begin = 0, end = 0.9, option = "A") + guides(fill = guide_legend(reverse=T)) + theme(legend.position = "none")

(p1 | p2)
```

Moving on!

# Cranial Size Estimate
```{r}
cf <- cdat %>% 
  select(c(Species, .draw, cCsize)) 

amb_nni <- get_mnni(cf, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(cf, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(cf, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(cf, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(cf, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(cf, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(cf, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(cf, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(cf, sptor) %>%  mutate(com = "Torompupu" )


nn_csize <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(csize_nn = value)

dd <- nn_csize %>% select(csize_nn)
adat <- adat  %>% bind_cols(dd)

```




# Dentary Nearest Neighbor

```{r}
ddat <- read_csv(here("Dentary_Data", "Dentary_20axes_Fitted.csv"))
```


#### Broken Stick
```{r}
a = rep(1:20)
#these are the PC variance values for the dentary Procrustes PCA
true = c(0.2821, 0.1529, 0.1424, 0.0693, 0.0548, 0.0393, 0.0345, 0.0269, 0.0241, 0.0212, 0.0173, 0.0164, 0.0126, 0.0117, 0.0102, 0.0097, 0.0089, 0.0082, 0.0066, 0.0059)
expected = PCDimension::brokenStick(1:20, 20)
d_bs = data.frame(a, true, expected)
d_bs %>% round(digits = 3)
```
Keep the first 3 PCs of the dentary shape.

#### Dentary NN Estimate
Estimate Dentary Shape Nearest Neighbor for each community
```{r}
df <- ddat %>% 
  select(c(Species, .draw, dPC1, dPC2, dPC3)) 

amb_nni <- get_mnni(df, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(df, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(df, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(df, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(df, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(df, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(df, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(df, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(df, sptor) %>%  mutate(com = "Torompupu" )

myx <- "Mean Nearest Neighbor Distance"

nn_dent <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(d_nn = value)

dd <- nn_dent %>% select(d_nn)
adat <- adat  %>% bind_cols(dd)
```


Very similar to cranial!

## Dentary Size Estimate
```{r}
df <- ddat %>% 
  select(c(Species, .draw, dCsize)) 

amb_nni <- get_mnni(df, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(df, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(df, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(df, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(df, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(df, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(df, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(df, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(df, sptor) %>%  mutate(com = "Torompupu" )

nn_dsize <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(dsize_nn = value)


dd <- nn_dsize %>% select(dsize_nn)
adat <- adat  %>% bind_cols(dd)
```




#Skull Nearest Neighbor
How do I do this?
```{r}
skdat <- ddat  %>% select(!.row) %>% 
  full_join(cdat, by = c(".draw", "Species"))
```
I guess I need to figure a way around the NAs
The only issue is the Paucidentomys in Latimojong and Gandang

## Skull NN Estimate
```{r}
df <- skdat %>% 
  select(c(Species, .draw, dPC1, dPC2, dPC3, cPC1, cPC2)) 

amb_nni <- get_mnni(df, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(df, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(df, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(df, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(df, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(df, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(df, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(df, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(df, sptor) %>%  mutate(com = "Torompupu" )

nn_sk <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(sk_nn = value)

rm(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni)

dd <- nn_sk %>% select(sk_nn)
adat <- adat %>% bind_cols(dd)
```



# External Measurements

```{r}
edat <- read_csv(here("External_Measurement_Data", "External_Fitted.csv"))
```

## Head-Body NN
```{r}
df <- edat %>% 
  select(c(Species, .draw, HB)) 

amb_nni <- get_mnni(df, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(df, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(df, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(df, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(df, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(df, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(df, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(df, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(df, sptor) %>%  mutate(com = "Torompupu" )

nn_HB <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(HB_nn = value)

dd <- nn_HB %>% select(HB_nn)
adat <- adat %>% bind_cols(dd)

nn_HB %>% 
  mutate(com = factor(com, level = level_order)) %>% 
 ggplot(aes(y = factor(com, level = level_order), x = 1/HB_nn, fill = com)) +
  stat_halfeye(.width = c(0.74, 0.89),  alpha = 0.7) +
   labs(title="HB",x="Mean Nearest Neighbor Distance", y = "", fill = "Mountain") +
  xlim(2, 11) +
  theme_bw() + scale_fill_viridis_d(direction = -1, begin = 0, end = 0.9, option = "A") + guides(fill = guide_legend(reverse=T)) + theme(legend.position = "none") 
```

## Tail NN
```{r}
df <- edat %>% 
  select(c(Species, .draw, rTail)) 

amb_nni <- get_mnni(df, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(df, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(df, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(df, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(df, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(df, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(df, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(df, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(df, sptor) %>%  mutate(com = "Torompupu" )

nn_Tail <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(Tail_nn = value)

dd <- nn_Tail %>% select(Tail_nn)
adat <- adat %>% bind_cols(dd)
```

## HF NN
```{r}
df <- edat %>% 
  select(c(Species, .draw, rHF)) 

amb_nni <- get_mnni(df, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(df, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(df, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(df, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(df, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(df, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(df, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(df, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(df, sptor) %>%  mutate(com = "Torompupu" )

nn_HF <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(HF_nn = value)

dd <- nn_HF %>% select(HF_nn)
adat <- adat %>% bind_cols(dd)
```


## Ear NN
```{r}
df <- edat %>% 
  select(c(Species, .draw, rEar)) 

amb_nni <- get_mnni(df, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(df, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(df, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(df, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(df, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(df, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(df, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(df, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(df, sptor) %>%  mutate(com = "Torompupu" )

nn_Ear <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(Ear_nn = value)

dd <- nn_Ear %>% select(Ear_nn)
adat <- adat %>% bind_cols(dd)
```

## Mass NN
```{r}
df <- edat %>% 
  select(c(Species, .draw, lMass)) 

amb_nni <- get_mnni(df, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(df, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(df, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(df, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(df, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(df, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(df, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(df, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(df, sptor) %>%  mutate(com = "Torompupu" )

nn_Mass <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(Mass_nn = value)

dd <- nn_Mass %>% select(Mass_nn)
adat <- adat %>% bind_cols(dd)
```


## Bsz NN
```{r}
df <- edat %>% 
  select(c(Species, .draw, lMass, HB)) 

amb_nni <- get_mnni(df, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(df, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(df, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(df, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(df, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(df, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(df, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(df, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(df, sptor) %>%  mutate(com = "Torompupu" )

nn_Bsz <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(Bsz_nn = value)

dd <- nn_Bsz %>% select(Bsz_nn)
adat <- adat %>% bind_cols(dd)
```

## All External NN

```{r}
df <- edat %>% 
  select(c(Species, .draw, HB, rTail, rHF, rEar, lMass)) 

amb_nni <- get_mnni(df, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(df, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(df, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(df, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(df, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(df, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(df, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(df, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(df, sptor) %>%  mutate(com = "Torompupu" )

nn_ext <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(ext_nn = value)

dd <- nn_ext %>% select(ext_nn)
adat <- adat %>% bind_cols(dd)
```

# Morpho NN
This is skull shape and external measurements hb, tail, hf, lmass, ear

```{r}
morph_dat <-  skdat  %>% select(!.row) %>% select(Species, .draw, dPC1, dPC2, dPC3, cPC1, cPC2) %>% 
  full_join(edat, by = c(".draw", "Species"))


df <- morph_dat %>% 
  select(!.row) 

amb_nni <- get_mnni(df, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(df, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(df, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(df, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(df, spgan) %>%  mutate(com = "Gandangdewata" )
kat_nni <- get_mnni(df, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(df, splat) %>%  mutate(com = "Latimojong" )
nok_nni <- get_mnni(df, spnok) %>%  mutate(com = "Nokilalaki" )
tor_nni <- get_mnni(df, sptor) %>%  mutate(com = "Torompupu" )

nn_morph <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni) %>% rename(morpho_nn = value)

dd <- nn_morph %>% select(morpho_nn)
adat <- adat %>% bind_cols(dd)


rm(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, kat_nni, lat_nni, nok_nni, tor_nni)
```


```{r}
adat %>% write_csv(here("All_Traits.csv"))
```

# Isotope GROUP Nearest Neighbor

Realized I have to use the grouping data again. Thats ok. It'll be just like any of the other variables.
## N15 Group
```{r}
idat <- read_csv(here("Isotope_Data", "Isotope_Group_Level_Fitted.csv")) %>% select(Species, .draw, sN15)


amb_nni <- get_mnni(idat, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(idat, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(idat, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(idat, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(idat, spgan) %>%  mutate(com = "Gandangdewata" )
#kat_nni <- get_mnni(idat, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(idat, splat) %>%  mutate(com = "Latimojong" )
#nok_nni <- get_mnni(idat, spnok) %>%  mutate(com = "Nokilalaki" )
#tor_nni <- get_mnni(idat, sptor) %>%  mutate(com = "Torompupu" )


nn_N <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, lat_nni) %>% rename(N15_nn_group = value) %>% mutate(.draw = rep(1:4000, 6))

adat <- adat  %>% 
  full_join(nn_N, by = c(".draw", "com"))
```

## C13 Group
```{r}
idat <- read_csv(here("Isotope_Data", "Isotope_Group_Level_Fitted.csv")) %>% select(Species, .draw, sC13)


amb_nni <- get_mnni(idat, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(idat, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(idat, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(idat, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(idat, spgan) %>%  mutate(com = "Gandangdewata" )
#kat_nni <- get_mnni(idat, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(idat, splat) %>%  mutate(com = "Latimojong" )
#nok_nni <- get_mnni(idat, spnok) %>%  mutate(com = "Nokilalaki" )
#tor_nni <- get_mnni(idat, sptor) %>%  mutate(com = "Torompupu" )


nn_C <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, lat_nni) %>% rename(C13_nn_group = value) %>% mutate(.draw = rep(1:4000, 6))

adat <- adat  %>% 
  full_join(nn_C, by = c(".draw", "com"))
```

## Iso Group
```{r}
idat <- read_csv(here("Isotope_Data", "Isotope_Group_Level_Fitted.csv")) %>% select(Species, .draw, sC13, sN15)


amb_nni <- get_mnni(idat, spamb) %>%  mutate(com = "Ambang" )
baw_nni <- get_mnni(idat, spbaw) %>%  mutate(com = "Bawakaraeng" )
bul_nni <- get_mnni(idat, spbul) %>%  mutate(com = "Buliohuto" )
dak_nni <- get_mnni(idat, spdak) %>%  mutate(com = "Dako" )
gan_nni <- get_mnni(idat, spgan) %>%  mutate(com = "Gandangdewata" )
#kat_nni <- get_mnni(idat, spkat) %>%  mutate(com = "Katopasa" )
lat_nni <- get_mnni(idat, splat) %>%  mutate(com = "Latimojong" )
#nok_nni <- get_mnni(idat, spnok) %>%  mutate(com = "Nokilalaki" )
#tor_nni <- get_mnni(idat, sptor) %>%  mutate(com = "Torompupu" )


nn_i <- bind_rows(amb_nni, baw_nni, bul_nni, dak_nni, gan_nni, lat_nni) %>% rename(iso_nn_group = value) %>% mutate(.draw = rep(1:4000, 6))

adat <- adat  %>% 
  full_join(nn_i, by = c(".draw", "com"))
```

#Write All Data
```{r}
adat %>% write_csv(here("All_Traits.csv"))
```
