---
title: "MNND_Randomization With Constrained Sampling Probabilities"
---

Randomization of NN Density values, but **CONSTRAINED** to fall into the overall convex hull of the community. This is the *constrained null model* of Swenson and Weiser 2014, On the packing and filling of functional space in eastern North American tree assemblages



```{r echo = FALSE}
pacman::p_load(here, tidyverse, tidybayes, patchwork, modelr, forcats, picante, furrr, dispRity, vegan)
#supress dplyr messages for summarise()
options(dplyr.summarise.inform = FALSE, readr.show_types = FALSE)

here::i_am('Code/Randomization_Density.Rmd')

load(here("Species_Data", "Species_Lists.RData"))
load(here("Species_Data", "Species_Extant.RData"))

ldat <-  read_csv(here("Locomotion_Data", "Locomotion_List.csv")) # List of species modes
lvdat <- read_csv(here("Locomotion_Data", "All_Locomotor_Var.csv")) #matrix for independent swap

sp_ses <- read.csv(here("Phylogenetic_Diversity", "Species_SES.csv")) %>% select(!X)

adat <- read_csv(here("All_Traits.csv"))


# Misc. infoprmation
n_sp <- tibble(com = c("Ambang", "Bawakaraeng", "Buliohuto", "Dako", "Gandangdewata", "Katopasa", "Latimojong", "Nokilalaki", "Torompupu"),
               num = c(13, 7, 10, 12, 23, 12, 13, 17, 15))

level_order <-  c( "Bawakaraeng", "Buliohuto", "Dako", "Katopasa", "Ambang", "Latimojong", "Torompupu", "Nokilalaki", "Gandangdewata")

```


# Constrained Species Lists


### Load Data and Estimate Means
```{r}

#External Data
m_edat <- read_csv(here("External_Measurement_Data", "External_Fitted.csv")) %>% 
  group_by(Species) %>% 
  summarise(across(HB:lMass, ~ mean(.x, na.rm = TRUE)))
# Cranial Data
m_cdat <- read_csv(here("Cranial_Data", "Cranial_36axes_Fitted.csv")) %>%
  mutate_if(is.numeric, round, digits=6) %>% 
  group_by(Species) %>% 
  summarise(across(cPC1:cPC2, ~ mean(.x, na.rm = TRUE)))
# Dentary Data
m_ddat <- read_csv(here("Dentary_Data", "Dentary_20axes_Fitted.csv")) %>%
  mutate_if(is.numeric, round, digits=6) %>% 
  group_by(Species) %>% 
  summarise(across(dPC1:dPC3, ~ mean(.x, na.rm = TRUE)))
```

### Get max and min values for each community for each trait

```{r}
min_max <- list(
  min = ~min(.x, na.rm = TRUE), 
  max = ~max(.x, na.rm = TRUE)
)

mn_mx <- function(sp, data, mountain){
data %>% 
    filter(Species %in% {{sp}}) %>% 
  summarise(across(where(is.numeric), min_max)) %>% 
    add_column(com = {{mountain}})
}

com_ls <- list(spamb, spbaw, spbul, spdak, spgan, spkat, splat, spnok, sptor)
mon_ls <- c("Ambang", "Bawakaraeng", "Buliohuto", "Dako", "GandangDewata", "Katopasa", "Latimojong", "Nokilalaki", "Torompupu")

e <- map2(com_ls, mon_ls, ~ mn_mx(.x, m_edat, .y)) %>% bind_rows()
c <- map2(com_ls, mon_ls, ~ mn_mx(.x, m_cdat, .y)) %>% bind_rows()
d <- map2(com_ls, mon_ls, ~ mn_mx(.x, m_ddat, .y)) %>% bind_rows()

maxmins <- full_join(e, d, by = "com") %>% 
  full_join(., c, by = "com") %>% relocate(com)
```

### Get species lists

This is tricky, I don't know the best way so I'll brute force it.
First, combine morpho data
```{r}
tt <- m_edat %>% full_join(m_cdat, by = "Species")
mean_all <- tt  %>% full_join(m_ddat, by = "Species")
```

#### For Loop
This filters by the max and min values for each communitiy for each measurement. 

```{r}
dlist <- list()
for (i in 1:9){
  dat1 <- mean_all %>% 
  filter(case_when(
    HB    > maxmins$HB_max[i]     ~ F,
    HB    < maxmins$HB_min[i]     ~ F,
    is.na(HB) ~ T,
    rTail > maxmins$rTail_max[i]  ~ F,
    rTail < maxmins$rTail_min[i]  ~ F,
    is.na(rTail) ~ T,
    rHF   > maxmins$rHF_max[i]    ~ F,
    rHF   < maxmins$rHF_min[i]    ~ F,
    is.na(rHF) ~ T,
    rEar  > maxmins$rEar_max[i]   ~ F,
    rEar  < maxmins$rEar_min[i]   ~ F,
    is.na(rEar) ~ T,
    lMass > maxmins$lMass_max[i]  ~ F,
    lMass < maxmins$lMass_min[i]  ~ F,
    is.na(lMass) ~ T,
    cPC1  > maxmins$cPC1_max[i]   ~ F,
    cPC1  < maxmins$cPC1_min[i]   ~ F,
    is.na(cPC1) ~ T,
    cPC2  > maxmins$cPC2_max[i]       ~ F,
    cPC2  < maxmins$cPC2_min[i]       ~ F,
    is.na(cPC2) ~ T,
    dPC1  > maxmins$dPC1_max[i]   ~ F,
    dPC1  < maxmins$dPC1_min[i]   ~ F,
    is.na(dPC1) ~ T,
    dPC2  > maxmins$dPC2_max[i]       ~ F,
    dPC2  < maxmins$dPC2_min[i]       ~ F,
    is.na(dPC2) ~ T,
    dPC3  > maxmins$dPC3_max[i]       ~ F,
    dPC3  < maxmins$dPC3_min[i]       ~ F,
     is.na(dPC3) ~ T,
    TRUE ~ T)) %>% select(Species) %>% as.vector()
  dlist[i] <- dat1
}
names(dlist) <- NULL
names(dlist) <- maxmins$com
```


# Sample Species

New sample species using independent swap algorithm from picante
Now I'm limiting it to the species in the `dlist` for each community that have overlapping morphological values. 
```{r}
sample_com <- function(com, list) {
dlist <- list()
for (i in 1:10){
  #THIS IS THE PART I CHANGED
  sp_ses <- subset(sp_ses, select = names(sp_ses) %in% {{list}})
  # This is unchanged
  b <- picante::randomizeMatrix(sp_ses, null.model = "trialswap", iterations = 1000) %>% 
    as_tibble() %>% 
    bind_cols(com = c("Ambang", "Bawakaraeng", "Buliohuto", "Dako", "Gandangdewata", "Katopasa", "Latimojong", "Nokilalaki", "Torompupu")) %>% 
    pivot_longer(cols = -com, names_to = 'species') %>%
    filter(as.logical(value)) %>%
    select(-value) %>%
    filter(com == {{com}}) %>% 
    select(-com) %>%
    pull(species)
  dlist[[i]] <- b
  }
dlist
}
```

Here i need to add the list of overlapping species
```{r}
sp_amb <- sample_com("Ambang", dlist$Ambang )
sp_baw <- sample_com("Bawakaraeng", dlist$Bawakaraeng)
sp_bul <- sample_com("Buliohuto", dlist$Buliohuto )
sp_dak <- sample_com("Dako", dlist$Dako )
sp_gan <- sample_com("Gandangdewata", dlist$GandangDewata )
sp_kat <- sample_com("Katopasa", dlist$Katopasa)
sp_lat <- sample_com("Latimojong", dlist$Latimojong)
sp_nok <- sample_com("Nokilalaki", dlist$Nokilalaki)
sp_tor <- sample_com("Torompupu", dlist$Torompupu)
```

# MNND Function
ALong with edits to two DispaRity functions to allow NA
```{r}
neighbours2 <- function(matrix, which = min, method = "euclidean") {
    distances <- as.matrix(check.dist.matrix2(matrix, method = method)[[1]])
    diag(distances) <- NA
    return(unname(apply(distances, 1, which, na.rm = TRUE)))
}

check.dist.matrix2 <- function(matrix, method, just.check = FALSE, ...) {
    was_dist <- FALSE
    if(is(matrix, "dist")) {
        return(list(matrix, "was_dist" = TRUE))
    }
    if(dim(matrix)[1] == dim(matrix)[2] &&
       all(diag(as.matrix(matrix)) == 0) &&
       all(matrix[upper.tri(matrix)] == matrix[rev(lower.tri(matrix))])) {
        was_dist <- TRUE
    }
    if(just.check) {
        return(was_dist)
    } else {
        if(was_dist) {
            return(list(stats::as.dist(matrix), "was_dist" = TRUE))
        } else {
          #Only change is here: na.rm=TRUE
            return(list(vegan::vegdist(matrix, method = method, na.rm = TRUE, ...), "was_dist" = FALSE))
        }
    }
}

get_mnni <- function(sp, data, mountain) {
  data %>% 
    filter(Species %in% {{sp}}) %>% 
  split(.$.draw) %>% 
  map(., ~ .x[ ,-c(1:2)])  %>% 
  map(~ .x %>%
        neighbours2() %>%
        #unique() %>% 
        mean()
        ) %>% 
  unlist() %>% 
  as_tibble() %>% 
  sample_n(., size = 100) %>% 
    add_column(com = {{mountain}})
}

```


# Skull Measurements  

#### Cranial Shape NN Estimation
This is using the variance Using PC1 & 2. Broken stick analysis is in `Models_Fitted_Density.Rmd`
```{r}
# Parallel computing options
furrr_options(seed = TRUE)
options(future.rng.onMisuse="ignore")
plan(multisession, workers = 4)

cdat <- read_csv(here("Cranial_Data", "Cranial_36axes_Fitted.csv")) %>% 
  select(c(Species, .draw, cPC1, cPC2)) 
cskamb <- future_map(sp_amb, ~ get_mnni(.x, cdat, "Ambang"), chunks = 1000) %>% bind_rows()
cskbaw <- future_map(sp_baw, ~ get_mnni(.x, cdat, "Bawakaraeng"), chunks = 1000) %>% bind_rows()
cskbul <- future_map(sp_bul, ~ get_mnni(.x, cdat, "Buliohuto"), chunks = 1000) %>% bind_rows()
cskdak <- future_map(sp_dak, ~ get_mnni(.x, cdat, "Dako"), chunks = 1000) %>% bind_rows()
cskgan <- future_map(sp_gan, ~ get_mnni(.x, cdat, "Gandangdewata"), chunks = 1000) %>% bind_rows()
cskkat <- future_map(sp_kat, ~ get_mnni(.x, cdat, "Katopasa"), chunks = 1000) %>% bind_rows()
csklat <- future_map(sp_lat, ~ get_mnni(.x, cdat, "Latimojong"), chunks = 1000) %>% bind_rows()
csknok <- future_map(sp_nok, ~ get_mnni(.x, cdat, "Nokilalaki"), chunks = 1000) %>% bind_rows()
csktor <- future_map(sp_tor, ~ get_mnni(.x, cdat, "Torompupu"), chunks = 1000) %>% bind_rows()

plan(sequential)

nn_c_shp_rand <- bind_rows(cskamb, cskbaw, cskbul, cskdak, cskgan, cskkat, csklat, csknok, csktor)
rm(cskamb, cskbaw, cskbul, cskdak, cskgan, cskkat, csklat, csknok, csktor)
```



#### Cranial SES
```{r}
adat <- nn_c_shp_rand %>% group_by(com) %>% 
  summarise(mean = mean(value),
            sd = sd(value)) %>% 
  as.data.frame() %>% 
  right_join(adat, by="com") %>%
  mutate(c_nnses_c =  (c_nn - mean) / sd) %>% 
  select(!c(mean, sd))

rm(nn_c_shp_rand )

```

#### Dentary Shape NMMI Estimation
Using 20 axes not PCA
```{r}
ddat <- read_csv(here("Dentary_Data", "Dentary_20axes_Fitted.csv")) %>% 
  select(c(Species, .draw, dPC1, dPC2, dPC3)) 

# Parallel computing options
furrr_options(seed = TRUE)
options(future.rng.onMisuse="ignore")
plan(multisession, workers = 8)

dskamb <- future_map(sp_amb, ~ get_mnni(.x, ddat, "Ambang"), chunks = 1000) %>% bind_rows()
dskbaw <- future_map(sp_baw, ~ get_mnni(.x, ddat, "Bawakaraeng"), chunks = 1000) %>% bind_rows()
dskbul <- future_map(sp_bul, ~ get_mnni(.x, ddat, "Buliohuto"), chunks = 1000) %>% bind_rows()
dskdak <- future_map(sp_dak, ~ get_mnni(.x, ddat, "Dako"), chunks = 1000) %>% bind_rows()
dskgan <- future_map(sp_gan, ~ get_mnni(.x, ddat, "Gandangdewata"), chunks = 1000) %>% bind_rows()
dskkat <- future_map(sp_kat, ~ get_mnni(.x, ddat, "Katopasa"), chunks = 1000) %>% bind_rows()
dsklat <- future_map(sp_lat, ~ get_mnni(.x, ddat, "Latimojong"), chunks = 1000) %>% bind_rows()
dsknok <- future_map(sp_nok, ~ get_mnni(.x, ddat, "Nokilalaki"), chunks = 1000) %>% bind_rows()
dsktor <- future_map(sp_tor, ~ get_mnni(.x, ddat, "Torompupu"), chunks = 1000) %>% bind_rows()

plan(sequential)

nn_d_shp_rand <- bind_rows(dskamb, dskbaw, dskbul, dskdak, dskgan, dskkat, dsklat, dsknok, dsktor) 
rm(dskamb, dskbaw, dskbul, dskdak, dskgan, dskkat, dsklat, dsknok, dsktor)
```

#### Dentary Shape SES
```{r}
adat <- nn_d_shp_rand %>% group_by(com) %>% 
  summarise(mean = mean(value),
            sd = sd(value)) %>% 
  as.data.frame() %>% 
  right_join(adat, by="com") %>%
  #select(!c_nnses_d) %>% 
  mutate(c_nnses_d =  (d_nn - mean) / sd) %>% 
  select(!c(mean, sd))

rm(nn_d_shp_rand )
```

#### Cranial Size NMMD Estimation
```{r}
cdat <- read_csv(here("Cranial_Data", "Cranial_36axes_Fitted.csv")) %>% 
  select(c(.draw, Species, cCsize))

# Parallel computing options
furrr_options(seed = TRUE)
options(future.rng.onMisuse="ignore")
plan(multisession, workers = 8)

cszamb <- future_map(sp_amb, ~ get_mnni(.x, cdat, "Ambang"), chunks = 1000) %>% bind_rows()
cszbaw <- future_map(sp_baw, ~ get_mnni(.x, cdat, "Bawakaraeng"), chunks = 1000) %>% bind_rows()
cszbul <- future_map(sp_bul, ~ get_mnni(.x, cdat, "Buliohuto"), chunks = 1000) %>% bind_rows()
cszdak <- future_map(sp_dak, ~ get_mnni(.x, cdat, "Dako"), chunks = 1000) %>% bind_rows()
cszgan <- future_map(sp_gan, ~ get_mnni(.x, cdat, "Gandangdewata"), chunks = 1000) %>% bind_rows()
cszkat <- future_map(sp_kat, ~ get_mnni(.x, cdat, "Katopasa"), chunks = 1000) %>% bind_rows()
cszlat <- future_map(sp_lat, ~ get_mnni(.x, cdat, "Latimojong"), chunks = 1000) %>% bind_rows()
csznok <- future_map(sp_nok, ~ get_mnni(.x, cdat, "Nokilalaki"), chunks = 1000) %>% bind_rows()
csztor <- future_map(sp_tor, ~ get_mnni(.x, cdat, "Torompupu"), chunks = 1000) %>% bind_rows()

plan(sequential)

nn_c_sz_rand <- bind_rows(cszamb, cszbaw, cszbul, cszdak, cszgan, cszkat, cszlat, csznok, csztor) 
rm(cszamb, cszbaw, cszbul, cszdak, cszgan, cszkat, cszlat, csznok, csztor)
```

#### Cranial Size SES

```{r}
adat <- nn_c_sz_rand %>% group_by(com) %>% 
  summarise(mean = mean(value),
            sd = sd(value)) %>% 
  as.data.frame() %>% 
  right_join(adat, by="com") %>%
  mutate(c_nnses_csize =  (csize_nn - mean) / sd) %>% 
  select(!c(mean, sd))

rm(nn_c_sz_rand)

```

#### Dentary Size NMMD Estimation
```{r}
ddat <- read_csv(here("Dentary_Data", "Dentary_20axes_Fitted.csv")) %>% 
  select(c(.draw, Species, dCsize))

# Parallel computing options
furrr_options(seed = TRUE)
options(future.rng.onMisuse="ignore")
plan(multisession, workers = 8)

dszamb <- future_map(sp_amb, ~ get_mnni(.x, ddat, "Ambang"), chunks = 1000) %>% bind_rows()
dszbaw <- future_map(sp_baw, ~ get_mnni(.x, ddat, "Bawakaraeng"), chunks = 1000) %>% bind_rows()
dszbul <- future_map(sp_bul, ~ get_mnni(.x, ddat, "Buliohuto"), chunks = 1000) %>% bind_rows()
dszdak <- future_map(sp_dak, ~ get_mnni(.x, ddat, "Dako"), chunks = 1000) %>% bind_rows()
dszgan <- future_map(sp_gan, ~ get_mnni(.x, ddat, "Gandangdewata"), chunks = 1000) %>% bind_rows()
dszkat <- future_map(sp_kat, ~ get_mnni(.x, ddat, "Katopasa"), chunks = 1000) %>% bind_rows()
dszlat <- future_map(sp_lat, ~ get_mnni(.x, ddat, "Latimojong"), chunks = 1000) %>% bind_rows()
dsznok <- future_map(sp_nok, ~ get_mnni(.x, ddat, "Nokilalaki"), chunks = 1000) %>% bind_rows()
dsztor <- future_map(sp_tor, ~ get_mnni(.x, ddat, "Torompupu"), chunks = 1000) %>% bind_rows()

plan(sequential)

nn_d_sz_rand <- bind_rows(dszamb, dszbaw, dszbul, dszdak, dszgan, dszkat, dszlat, dsznok, dsztor) 
rm(dszamb, dszbaw, dszbul, dszdak, dszgan, dszkat, dszlat, dsznok, dsztor)
```

#### Dentary Size SES
```{r}
adat <- nn_d_sz_rand %>% group_by(com) %>% 
  summarise(mean = mean(value),
            sd = sd(value)) %>% 
  as.data.frame() %>% 
  right_join(adat, by="com") %>%
  #select(!c_nnses_dsize) %>% 
  mutate(c_nnses_dsize =  (dsize_nn - mean) / sd) %>% 
  select(!c(mean, sd))

rm(nn_d_sz_rand)

```

## Skull Shape NMMI
```{r}
cdat <- read_csv(here("Cranial_Data", "Cranial_36axes_Fitted.csv")) %>% 
  select(c(Species, .draw, cPC1, cPC2)) 
ddat <- read_csv(here("Dentary_Data", "Dentary_20axes_Fitted.csv")) %>% 
  select(c(Species, .draw, dPC1, dPC2, dPC3))
skdat <- ddat  %>% #select(!.row) %>% 
  full_join(cdat, by = c(".draw", "Species"))
rm(cdat, ddat)

# Parallel computing options
furrr_options(seed = TRUE)
options(future.rng.onMisuse="ignore")
plan(multisession, workers = 8)

skamb <- future_map(sp_amb, ~ get_mnni(.x, skdat, "Ambang"), chunks = 1000) %>% bind_rows()
skbaw <- future_map(sp_baw, ~ get_mnni(.x, skdat, "Bawakaraeng"), chunks = 1000) %>% bind_rows()
skbul <- future_map(sp_bul, ~ get_mnni(.x, skdat, "Buliohuto"), chunks = 1000) %>% bind_rows()
skdak <- future_map(sp_dak, ~ get_mnni(.x, skdat, "Dako"), chunks = 1000) %>% bind_rows()
skgan <- future_map(sp_gan, ~ get_mnni(.x, skdat, "Gandangdewata"), chunks = 1000) %>% bind_rows()
skkat <- future_map(sp_kat, ~ get_mnni(.x, skdat, "Katopasa"), chunks = 1000) %>% bind_rows()
sklat <- future_map(sp_lat, ~ get_mnni(.x, skdat, "Latimojong"), chunks = 1000) %>% bind_rows()
sknok <- future_map(sp_nok, ~ get_mnni(.x, skdat, "Nokilalaki"), chunks = 1000) %>% bind_rows()
sktor <- future_map(sp_tor, ~ get_mnni(.x, skdat, "Torompupu"), chunks = 1000) %>% bind_rows()


plan(sequential)

nn_sk_rand <- bind_rows(skamb, skbaw, skbul, skdak, skgan, skkat, sklat, sknok, sktor) 
rm(skamb, skbaw, skbul, skdak, skgan, skkat, sklat, sknok, sktor)
```

### Skull Shape SES
```{r}
adat <- nn_sk_rand %>% group_by(com) %>% 
  summarise(mean = mean(value),
            sd = sd(value)) %>% 
  as.data.frame() %>% 
  right_join(adat, by="com") %>%
  #select(!c_nnses_sk) %>% 
  mutate(c_nnses_sk =  (sk_nn - mean) / sd) %>% 
  select(!c(mean, sd))

rm(nn_sk_rand )
```


# External Shape
#### Body Size
```{r}
xdat <- read_csv(here("External_Measurement_Data", "External_Fitted.csv")) %>% 
  select(-.row) %>% 
  select(Species, .draw, HB, lMass)

# Parallel computing options
furrr_options(seed = TRUE)
options(future.rng.onMisuse="ignore")
plan(multisession, workers = 8)

bszamb <- future_map(sp_amb, ~ get_mnni(.x, xdat, "Ambang"), chunks = 1000) %>% bind_rows()
bszbaw <- future_map(sp_baw, ~ get_mnni(.x, xdat, "Bawakaraeng"), chunks = 1000) %>% bind_rows()
bszbul <- future_map(sp_bul, ~ get_mnni(.x, xdat, "Buliohuto"), chunks = 1000) %>% bind_rows()
bszdak <- future_map(sp_dak, ~ get_mnni(.x, xdat, "Dako"), chunks = 1000) %>% bind_rows()
bszgan <- future_map(sp_gan, ~ get_mnni(.x, xdat, "Gandangdewata"), chunks = 1000) %>% bind_rows()
bszkat <- future_map(sp_kat, ~ get_mnni(.x, xdat, "Katopasa"), chunks = 1000) %>% bind_rows()
bszlat <- future_map(sp_lat, ~ get_mnni(.x, xdat, "Latimojong"), chunks = 1000) %>% bind_rows()
bsznok <- future_map(sp_nok, ~ get_mnni(.x, xdat, "Nokilalaki"), chunks = 1000) %>% bind_rows()
bsztor <- future_map(sp_tor, ~ get_mnni(.x, xdat, "Torompupu"), chunks = 1000) %>% bind_rows()

plan(sequential)

nn_b_sz_rand <- bind_rows(bszamb, bszbaw, bszbul, bszdak, bszgan, bszkat, bszlat, bsznok, bsztor)
rm(bszamb, bszbaw, bszbul, bszdak, bszgan, bszkat, bszlat, bsznok, bsztor)
```

#### Body Size SES
```{r}
adat <- nn_b_sz_rand %>% group_by(com) %>% 
  summarise(mean = mean(value),
            sd = sd(value)) %>% 
  as.data.frame() %>% 
  right_join(adat, by="com") %>%
  #select(!c_nnses_Bsz) %>% 
  mutate(c_nnses_Bsz =  (Bsz_nn - mean) / sd) %>% 
  select(!c(mean, sd))

rm(nn_b_sz_rand)

```


#### Tail
```{r}
xdat <- read_csv(here("External_Measurement_Data", "External_Fitted.csv")) %>% 
  select(-.row) %>%
  select(Species, .draw, rTail)

# Parallel computing options
furrr_options(seed = TRUE)
options(future.rng.onMisuse="ignore")
plan(multisession, workers = 8)

tailamb <- future_map(sp_amb, ~ get_mnni(.x, xdat, "Ambang"), chunks = 1000) %>% bind_rows()
tailbaw <- future_map(sp_baw, ~ get_mnni(.x, xdat, "Bawakaraeng"), chunks = 1000) %>% bind_rows()
tailbul <- future_map(sp_bul, ~ get_mnni(.x, xdat, "Buliohuto"), chunks = 1000) %>% bind_rows()
taildak <- future_map(sp_dak, ~ get_mnni(.x, xdat, "Dako"), chunks = 1000) %>% bind_rows()
tailgan <- future_map(sp_gan, ~ get_mnni(.x, xdat, "Gandangdewata"), chunks = 1000) %>% bind_rows
tailkat <- future_map(sp_kat, ~ get_mnni(.x, xdat, "Katopasa"), chunks = 1000) %>% bind_rows()
taillat <- future_map(sp_lat, ~ get_mnni(.x, xdat, "Latimojong"), chunks = 1000) %>% bind_rows()
tailnok <- future_map(sp_nok, ~ get_mnni(.x, xdat, "Nokilalaki"), chunks = 1000) %>% bind_rows()
tailtor <- future_map(sp_tor, ~ get_mnni(.x, xdat, "Torompupu"), chunks = 1000) %>% bind_rows()

plan(sequential)

nn_tail_rand <- bind_rows(tailamb, tailbaw, tailbul, taildak, tailgan, tailkat, taillat, tailnok, tailtor)
rm(tailamb, tailbaw, tailbul, taildak, tailgan, tailkat, taillat, tailnok, tailtor)
```

#### Tail SES
```{r}
adat <- nn_tail_rand %>% group_by(com) %>% 
  summarise(mean = mean(value),
            sd = sd(value)) %>% 
  as.data.frame() %>% 
  right_join(adat, by="com") %>%
  mutate(c_nnses_Tail =  (Tail_nn - mean) / sd) %>% 
  select(!c(mean, sd))

rm(nn_tail_rand)
```

#### Hind Foot
```{r}
xdat <- read_csv(here("External_Measurement_Data", "External_Fitted.csv")) %>% 
  select(-.row) %>%
  select(Species, .draw, rHF)

# Parallel computing options
furrr_options(seed = TRUE)
options(future.rng.onMisuse="ignore")
plan(multisession, workers = 8)

hfamb <- future_map(sp_amb, ~ get_mnni(.x, xdat, "Ambang"), chunks = 1000) %>% bind_rows()
hfbaw <- future_map(sp_baw, ~ get_mnni(.x, xdat, "Bawakaraeng"), chunks = 1000) %>% bind_rows()
hfbul <- future_map(sp_bul, ~ get_mnni(.x, xdat, "Buliohuto"), chunks = 1000) %>% bind_rows()
hfdak <- future_map(sp_dak, ~ get_mnni(.x, xdat, "Dako"), chunks = 1000) %>% bind_rows()
hfgan <- future_map(sp_gan, ~ get_mnni(.x, xdat, "Gandangdewata"), chunks = 1000) %>% bind_rows
hfkat <- future_map(sp_kat, ~ get_mnni(.x, xdat, "Katopasa"), chunks = 1000) %>% bind_rows()
hflat <- future_map(sp_lat, ~ get_mnni(.x, xdat, "Latimojong"), chunks = 1000) %>% bind_rows()
hfnok <- future_map(sp_nok, ~ get_mnni(.x, xdat, "Nokilalaki"), chunks = 1000) %>% bind_rows()
hftor <- future_map(sp_tor, ~ get_mnni(.x, xdat, "Torompupu"), chunks = 1000) %>% bind_rows()

plan(sequential)

nn_hf_rand <- bind_rows(hfamb, hfbaw, hfbul, hfdak, hfgan, hfkat, hflat, hfnok, hftor)
rm(hfamb, hfbaw, hfbul, hfdak, hfgan, hfkat, hflat, hfnok, hftor)
```

#### HF SES
```{r}
adat <- nn_hf_rand %>% group_by(com) %>% 
  summarise(mean = mean(value),
            sd = sd(value)) %>% 
  as.data.frame() %>% 
  right_join(adat, by="com") %>%
  mutate(c_nnses_HF =  (HF_nn - mean) / sd) %>% 
  select(!c(mean, sd))

rm(nn_hf_rand)

```

#### Ear
```{r}
xdat <- read_csv(here("External_Measurement_Data", "External_Fitted.csv")) %>% 
  select(-.row) %>%
  select(Species, .draw, rEar)

# Parallel computing options
furrr_options(seed = TRUE)
options(future.rng.onMisuse="ignore")
plan(multisession, workers = 8)

earamb <- future_map(sp_amb, ~ get_mnni(.x, xdat, "Ambang"), chunks = 1000) %>% bind_rows()
earbaw <- future_map(sp_baw, ~ get_mnni(.x, xdat, "Bawakaraeng"), chunks = 1000) %>% bind_rows()
earbul <- future_map(sp_bul, ~ get_mnni(.x, xdat, "Buliohuto"), chunks = 1000) %>% bind_rows()
eardak <- future_map(sp_dak, ~ get_mnni(.x, xdat, "Dako"), chunks = 1000) %>% bind_rows()
eargan <- future_map(sp_gan, ~ get_mnni(.x, xdat, "Gandangdewata"), chunks = 1000) %>% bind_rows
earkat <- future_map(sp_kat, ~ get_mnni(.x, xdat, "Katopasa"), chunks = 1000) %>% bind_rows()
earlat <- future_map(sp_lat, ~ get_mnni(.x, xdat, "Latimojong"), chunks = 1000) %>% bind_rows()
earnok <- future_map(sp_nok, ~ get_mnni(.x, xdat, "Nokilalaki"), chunks = 1000) %>% bind_rows()
eartor <- future_map(sp_tor, ~ get_mnni(.x, xdat, "Torompupu"), chunks = 1000) %>% bind_rows()

plan(sequential)

nn_ear_rand <- bind_rows(earamb, earbaw, earbul, eardak, eargan, earkat, earlat, earnok, eartor)
rm(earamb, earbaw, earbul, eardak, eargan, earkat, earlat, earnok, eartor)
```

#### Ear SES
```{r}
adat <- nn_ear_rand %>% group_by(com) %>% 
  summarise(mean = mean(value),
            sd = sd(value)) %>% 
  as.data.frame() %>% 
  right_join(adat, by="com") %>%
  mutate(c_nnses_Ear =  (Ear_nn - mean) / sd) %>% 
  select(!c(mean, sd))

rm(nn_ear_rand)
```

#### HB
```{r}
xdat <- read_csv(here("External_Measurement_Data", "External_Fitted.csv")) %>% 
  select(-.row) %>%
  select(Species, .draw, HB)

# Parallel computing options
furrr_options(seed = TRUE)
options(future.rng.onMisuse="ignore")
plan(multisession, workers = 8)

hbamb <- future_map(sp_amb, ~ get_mnni(.x, xdat, "Ambang"), chunks = 1000) %>% bind_rows()
hbbaw <- future_map(sp_baw, ~ get_mnni(.x, xdat, "Bawakaraeng"), chunks = 1000) %>% bind_rows()
hbbul <- future_map(sp_bul, ~ get_mnni(.x, xdat, "Buliohuto"), chunks = 1000) %>% bind_rows()
hbdak <- future_map(sp_dak, ~ get_mnni(.x, xdat, "Dako"), chunks = 1000) %>% bind_rows()
hbgan <- future_map(sp_gan, ~ get_mnni(.x, xdat, "Gandangdewata"), chunks = 1000) %>% bind_rows
hbkat <- future_map(sp_kat, ~ get_mnni(.x, xdat, "Katopasa"), chunks = 1000) %>% bind_rows()
hblat <- future_map(sp_lat, ~ get_mnni(.x, xdat, "Latimojong"), chunks = 1000) %>% bind_rows()
hbnok <- future_map(sp_nok, ~ get_mnni(.x, xdat, "Nokilalaki"), chunks = 1000) %>% bind_rows()
hbtor <- future_map(sp_tor, ~ get_mnni(.x, xdat, "Torompupu"), chunks = 1000) %>% bind_rows()

plan(sequential)

nn_hb_rand <- bind_rows(hbamb, hbbaw, hbbul, hbdak, hbgan, hbkat, hblat, hbnok, hbtor)
rm(hbamb, hbbaw, hbbul, hbdak, hbgan, hbkat, hblat, hbnok, hbtor)
```

#### HB SES
```{r}
adat <- nn_hb_rand %>% group_by(com) %>% 
  summarise(mean = mean(value),
            sd = sd(value)) %>% 
  as.data.frame() %>% 
  right_join(adat, by="com") %>%
  mutate(c_nnses_HB =  (HB_nn - mean) / sd) %>% 
  select(!c(mean, sd))

rm(nn_hb_rand )
```

#### Mass
```{r}
xdat <- read_csv(here("External_Measurement_Data", "External_Fitted.csv")) %>% 
  select(-.row) %>%
  select(Species, .draw, lMass)

# Parallel computing options
furrr_options(seed = TRUE)
options(future.rng.onMisuse="ignore")
plan(multisession, workers = 8)

massamb <- future_map(sp_amb, ~ get_mnni(.x, xdat, "Ambang"), chunks = 1000) %>% bind_rows()
massbaw <- future_map(sp_baw, ~ get_mnni(.x, xdat, "Bawakaraeng"), chunks = 1000) %>% bind_rows()
massbul <- future_map(sp_bul, ~ get_mnni(.x, xdat, "Buliohuto"), chunks = 1000) %>% bind_rows()
massdak <- future_map(sp_dak, ~ get_mnni(.x, xdat, "Dako"), chunks = 1000) %>% bind_rows()
massgan <- future_map(sp_gan, ~ get_mnni(.x, xdat, "Gandangdewata"), chunks = 1000) %>% bind_rows
masskat <- future_map(sp_kat, ~ get_mnni(.x, xdat, "Katopasa"), chunks = 1000) %>% bind_rows()
masslat <- future_map(sp_lat, ~ get_mnni(.x, xdat, "Latimojong"), chunks = 1000) %>% bind_rows()
massnok <- future_map(sp_nok, ~ get_mnni(.x, xdat, "Nokilalaki"), chunks = 1000) %>% bind_rows()
masstor <- future_map(sp_tor, ~ get_mnni(.x, xdat, "Torompupu"), chunks = 1000) %>% bind_rows()

plan(sequential)

nn_mass_rand <- bind_rows(massamb, massbaw, massbul, massdak, massgan, masskat, masslat, massnok, masstor)
rm(massamb, massbaw, massbul, massdak, massgan, masskat, masslat, massnok, masstor)
```

#### Mass SES
```{r}
adat <- nn_mass_rand %>% group_by(com) %>% 
  summarise(mean = mean(value),
            sd = sd(value)) %>% 
  as.data.frame() %>% 
  right_join(adat, by="com") %>%
  mutate(c_nnses_Mass =  (Mass_nn - mean) / sd) %>% 
  select(!c(mean, sd))

rm(nn_mass_rand)
```

#### Body Proportions Raw
```{r}
xdat <- read_csv(here("External_Measurement_Data", "External_Fitted.csv")) %>% 
  select(-.row) %>%
  select(Species, .draw, HB, rTail, rHF, rEar)

# Parallel computing options
furrr_options(seed = TRUE)
options(future.rng.onMisuse="ignore")
plan(multisession, workers = 8)

x_shpamb <- future_map(sp_amb, ~ get_mnni(.x, xdat, "Ambang"), chunks = 1000) %>% bind_rows()
x_shpbaw <- future_map(sp_baw, ~ get_mnni(.x, xdat, "Bawakaraeng"), chunks = 1000) %>% bind_rows()
x_shpbul <- future_map(sp_bul, ~ get_mnni(.x, xdat, "Buliohuto"), chunks = 1000) %>% bind_rows()
x_shpdak <- future_map(sp_dak, ~ get_mnni(.x, xdat, "Dako"), chunks = 1000) %>% bind_rows()
x_shpgan <- future_map(sp_gan, ~ get_mnni(.x, xdat, "Gandangdewata"), chunks = 1000) %>% bind_rows
x_shpkat <- future_map(sp_kat, ~ get_mnni(.x, xdat, "Katopasa"), chunks = 1000) %>% bind_rows()
x_shplat <- future_map(sp_lat, ~ get_mnni(.x, xdat, "Latimojong"), chunks = 1000) %>% bind_rows()
x_shpnok <- future_map(sp_nok, ~ get_mnni(.x, xdat, "Nokilalaki"), chunks = 1000) %>% bind_rows()
x_shptor <- future_map(sp_tor, ~ get_mnni(.x, xdat, "Torompupu"), chunks = 1000) %>% bind_rows()

plan(sequential)

nn_x_shp_rand <- bind_rows(x_shpamb, x_shpbaw, x_shpbul, x_shpdak, x_shpgan, x_shpkat, x_shplat, x_shpnok, x_shptor)
rm(x_shpamb, x_shpbaw, x_shpbul, x_shpdak, x_shpgan, x_shpkat, x_shplat, x_shpnok, x_shptor)
```

####Body Proportions SES

```{r}
adat <- nn_x_shp_rand %>% group_by(com) %>% 
  summarise(mean = mean(value),
            sd = sd(value)) %>% 
  as.data.frame() %>% 
  right_join(adat, by="com") %>%
  mutate(c_nnses_ext =  (ext_nn - mean) / sd) %>% 
  select(!c(mean, sd))

rm(nn_x_shp_rand)

```
# Morpho Shape

#### Morpho MNNI
```{r}
cdat <- read_csv(here("Cranial_Data", "Cranial_36axes_Fitted.csv")) %>% select(-.row) %>%
  select(c(Species, .draw, cPC1, cPC2))
ddat <- read_csv(here("Dentary_Data", "Dentary_20axes_Fitted.csv")) %>% select(-.row) %>%
  select(c(Species, .draw, dPC1, dPC2, dPC3)) 
xdat <- read_csv(here("External_Measurement_Data", "External_Fitted.csv")) %>% select(-.row) %>% 
  select(Species, .draw, HB, lMass, rTail, rEar, rHF)
skdat <- ddat  %>% full_join(cdat, by = c(".draw", "Species"))
morphdat <- xdat %>% full_join(skdat, by = c(".draw", "Species"))

rm(cdat, ddat, xdat)

# Parallel computing options
furrr_options(seed = TRUE)
options(future.rng.onMisuse="ignore")
plan(multisession, workers = 8)

mshpamb <- future_map(sp_amb, ~ get_mnni(.x, morphdat, "Ambang"), chunks = 1000) %>% bind_rows()
mshpbaw <- future_map(sp_baw, ~ get_mnni(.x, morphdat, "Bawakaraeng"), chunks = 1000) %>% bind_rows()
mshpbul <- future_map(sp_bul, ~ get_mnni(.x, morphdat, "Buliohuto"), chunks = 1000) %>% bind_rows()
mshpdak <- future_map(sp_dak, ~ get_mnni(.x, morphdat, "Dako"), chunks = 1000) %>% bind_rows()
mshpgan <- future_map(sp_gan, ~ get_mnni(.x, morphdat, "Gandangdewata"), chunks = 1000) %>% bind_rows
mshpkat <- future_map(sp_kat, ~ get_mnni(.x, morphdat, "Katopasa"), chunks = 1000) %>% bind_rows()
mshplat <- future_map(sp_lat, ~ get_mnni(.x, morphdat, "Latimojong"), chunks = 1000) %>% bind_rows()
mshpnok <- future_map(sp_nok, ~ get_mnni(.x, morphdat, "Nokilalaki"), chunks = 1000) %>% bind_rows()
mshptor <- future_map(sp_tor, ~ get_mnni(.x, morphdat, "Torompupu"), chunks = 1000) %>% bind_rows()

plan(sequential)

nn_mshp_rand <- bind_rows(mshpamb, mshpbaw, mshpbul, mshpdak, mshpgan, mshpkat, mshplat, mshpnok, mshptor)
rm(mshpamb, mshpbaw, mshpbul, mshpdak, mshpgan, mshpkat, mshplat, mshpnok, mshptor)
```
#### Morpho SES
```{r}
adat <- nn_mshp_rand %>% group_by(com) %>% 
  summarise(mean = mean(value),
            sd = sd(value)) %>% 
  as.data.frame() %>% 
  right_join(adat, by="com") %>%
  mutate(c_nnses_morpho =  (morpho_nn - mean) / sd) %>% 
  select(!c(mean, sd))

rm(nn_x_shp_rand)
```

# Isotopes
### There are some changes here
I want load in the community group_level fitted values for estimating the random communities. 

Need to resample the commuities here to limit the isotopes to species within community isotope space (ignoring morphology)
```{r}
idat <- read_csv(here("Isotope_Data", "Isotope_Group_Level_Fitted.csv")) 

m_idat <- read_csv(here("Isotope_Data", "Isotope_Group_Level_Fitted.csv")) %>% 
  group_by(Species) %>% 
  summarise(across(sN15:sC13, ~ mean(.x, na.rm = TRUE)))

```
### Get max and min values for each community for each trait

```{r}
min_max <- list(
  min = ~min(.x, na.rm = TRUE), 
  max = ~max(.x, na.rm = TRUE)
)

mn_mx <- function(sp, data, mountain){
data %>% 
    filter(Species %in% {{sp}}) %>% 
  summarise(across(where(is.numeric), min_max)) %>% 
    add_column(com = {{mountain}})
}

com_ls <- list(spamb, spbaw, spbul, spdak, spgan, spkat, splat, spnok, sptor)
mon_ls <- c("Ambang", "Bawakaraeng", "Buliohuto", "Dako", "GandangDewata", "Katopasa", "Latimojong", "Nokilalaki", "Torompupu")

maxmins <- map2(com_ls, mon_ls, ~ mn_mx(.x, m_idat, .y)) %>% bind_rows()

#maxmins <- full_join(e, d, by = "com") %>% 
  #full_join(., c, by = "com") %>% relocate(com)
```


#### For Loop
This filters by the max and min values for each communitiy for each measurement. 

```{r}
dlist <- list()
for (i in 1:9){
  dat1 <- m_idat %>% 
  filter(case_when(
    sN15    > maxmins$sN15_max[i]     ~ F,
    sN15    < maxmins$sN15_min[i]     ~ F,
    is.na(sN15) ~ T,
    sC13 > maxmins$sC13_max[i]  ~ F,
    sC13 < maxmins$sC13_min[i]  ~ F,
    is.na(sC13 ) ~ T,
    TRUE ~ T)) %>% select(Species) %>% as.vector()
  dlist[i] <- dat1
}
names(dlist) <- NULL
names(dlist) <- maxmins$com
```


### Sample Species

```{r}
sample_com <- function(com, list) {
dlist <- list()
for (i in 1:10){
  #THIS IS THE PART I CHANGED
  sp_ses <- subset(sp_ses, select = names(sp_ses) %in% {{list}})
  # This is unchanged
  b <- picante::randomizeMatrix(sp_ses, null.model = "trialswap", iterations = 1000) %>% 
    as_tibble() %>% 
    bind_cols(com = c("Ambang", "Bawakaraeng", "Buliohuto", "Dako", "Gandangdewata", "Katopasa", "Latimojong", "Nokilalaki", "Torompupu")) %>% 
    pivot_longer(cols = -com, names_to = 'species') %>%
    filter(as.logical(value)) %>%
    select(-value) %>%
    filter(com == {{com}}) %>% 
    select(-com) %>%
    pull(species)
  dlist[[i]] <- b
  }
dlist
}
```

Here i need to add the list of overlapping species
```{r}
sp_amb <- sample_com("Ambang", dlist$Ambang )
sp_baw <- sample_com("Bawakaraeng", dlist$Bawakaraeng)
sp_bul <- sample_com("Buliohuto", dlist$Buliohuto )
sp_dak <- sample_com("Dako", dlist$Dako )
sp_gan <- sample_com("Gandangdewata", dlist$GandangDewata )
sp_kat <- sample_com("Katopasa", dlist$Katopasa)
sp_lat <- sample_com("Latimojong", dlist$Latimojong)
sp_nok <- sample_com("Nokilalaki", dlist$Nokilalaki)
sp_tor <- sample_com("Torompupu", dlist$Torompupu)
```

#### Carbon
```{r}
idat <- read_csv(here("Isotope_Data", "Isotope_Group_Level_Fitted.csv")) %>% select(Species, .draw, sC13)

# Parallel computing options
furrr_options(seed = TRUE)
options(future.rng.onMisuse="ignore")
plan(multisession, workers = 8)

camb <- future_map(sp_amb, ~ get_mnni(.x, idat, "Ambang"), chunks = 1000) %>%  bind_rows()
cbaw <- future_map(sp_baw, ~ get_mnni(.x, idat, "Buliohuto"), chunks = 1000) %>%  bind_rows()
cbul <- future_map(sp_bul, ~ get_mnni(.x, idat, "Bawakaraeng"), chunks = 1000) %>%  bind_rows()
cdak <- future_map(sp_dak, ~ get_mnni(.x, idat, "Dako"), chunks = 1000) %>%  bind_rows()
cgan <- future_map(sp_gan, ~ get_mnni(.x, idat, "Gandangdewata"), chunks = 1000) %>%  bind_rows()
clat <- future_map(sp_lat, ~ get_mnni(.x, idat, "Latimojong"), chunks = 1000) %>%  bind_rows()

plan(sequential)

nn_car_rand <- bind_rows(camb, cbaw, cbul, cdak, cgan, clat)
rm(camb, cbaw, cbul, cdak, cgan, clat)
```

#### Carbon SES
then I am using the group-level model to generate mean and sd, then subtract from the RAW nn values
```{r}
adat <- nn_car_rand %>% group_by(com) %>% 
  summarise(mean = mean(value),
            sd = sd(value)) %>% 
  as.data.frame() %>% 
  right_join(adat, by="com") %>%
  mutate(c_nnses_C13 =  (C13_nn - mean) / sd) %>% 
  select(!c(mean, sd))
rm(nn_car_rand)
```


#### Nitrogen
```{r}
idat <- read_csv(here("Isotope_Data", "Isotope_Group_Level_Fitted.csv")) %>% select(Species, .draw, sN15)

# Parallel computing options
furrr_options(seed = TRUE)
options(future.rng.onMisuse="ignore")
plan(multisession, workers = 8)

camb <- future_map(sp_amb, ~ get_mnni(.x, idat, "Ambang"), chunks = 1000) %>%  bind_rows()
cbaw <- future_map(sp_baw, ~ get_mnni(.x, idat, "Buliohuto"), chunks = 1000) %>%  bind_rows()
cbul <- future_map(sp_bul, ~ get_mnni(.x, idat, "Bawakaraeng"), chunks = 1000) %>%  bind_rows()
cdak <- future_map(sp_dak, ~ get_mnni(.x, idat, "Dako"), chunks = 1000) %>%  bind_rows()
cgan <- future_map(sp_gan, ~ get_mnni(.x, idat, "Gandangdewata"), chunks = 1000) %>%  bind_rows()
clat <- future_map(sp_lat, ~ get_mnni(.x, idat, "Latimojong"), chunks = 1000) %>%  bind_rows()

plan(sequential)

nn_car_rand <- bind_rows(camb, cbaw, cbul, cdak, cgan, clat)
rm(camb, cbaw, cbul, cdak, cgan, clat)
```

#### Nitrogen SES
then I am using the group-level model to generate mean and sd, then subtract from the group nn values
```{r}
adat <- nn_car_rand %>% group_by(com) %>% 
  summarise(mean = mean(value),
            sd = sd(value)) %>% 
  as.data.frame() %>% 
  right_join(adat, by="com") %>%
  mutate(c_nnses_N15 =  (N15_nn - mean) / sd) %>% 
  select(!c(mean, sd))
rm(nn_car_rand)
```


#### Isotopic Niche
```{r}
idat <- read_csv(here("Isotope_Data", "Isotope_Group_Level_Fitted.csv")) %>% select(Species, .draw, sN15, sC13)

# Parallel computing options
furrr_options(seed = TRUE)
options(future.rng.onMisuse="ignore")
plan(multisession, workers = 8)

camb <- future_map(sp_amb, ~ get_mnni(.x, idat, "Ambang"), chunks = 1000) %>%  bind_rows()
cbaw <- future_map(sp_baw, ~ get_mnni(.x, idat, "Buliohuto"), chunks = 1000) %>%  bind_rows()
cbul <- future_map(sp_bul, ~ get_mnni(.x, idat, "Bawakaraeng"), chunks = 1000) %>%  bind_rows()
cdak <- future_map(sp_dak, ~ get_mnni(.x, idat, "Dako"), chunks = 1000) %>%  bind_rows()
cgan <- future_map(sp_gan, ~ get_mnni(.x, idat, "Gandangdewata"), chunks = 1000) %>%  bind_rows()
clat <- future_map(sp_lat, ~ get_mnni(.x, idat, "Latimojong"), chunks = 1000) %>%  bind_rows()

plan(sequential)

nn_car_rand <- bind_rows(camb, cbaw, cbul, cdak, cgan, clat)
rm(camb, cbaw, cbul, cdak, cgan, clat)
```

#### Isotopic Niche SES
```{r}
adat <- nn_car_rand %>% group_by(com) %>% 
  summarise(mean = mean(value),
            sd = sd(value)) %>% 
  as.data.frame() %>% 
  right_join(adat, by="com") %>%
  mutate(c_nnses_iso =  (iso_nn - mean) / sd) %>% 
  select(!c(mean, sd))
rm(nn_car_rand)
```

# Write Final data
```{r}
adat %>% write_csv(here("All_Traits.csv"))
```

# Locomotor NN SES
This is a little different. 

It makes a matrix with 4 locomotor columns, and binary data for each row(species)

This method is only used for the NN  and NNSES as Var works fine for 
```{r}
load(here("Species_Data", "Species_Lists.RData"))
load(here("Species_Data", "Species_Extant.RData"))
level_order <-  c( 'Bawakaraeng', 'Buliohuto','Dako', "Katopasa", "Ambang", "Latimojong", "Torompupu", "Nokilalaki", "Gandangdewata")
locdat <- read_csv(here("Locomotion_Data", "Locomotion_List.csv"))
d_locdat <- read_csv(here("Locomotion_Data", "Locomotion_Dummy.csv"))

```

### RDA Nearest Neighbor

Estimating an RDA from the dummy variable matrix

```{r}
d1 <- d_locdat %>% select(!Species)%>% rda(.)
r.d1  <- d1$CA$u %>% as_tibble() %>% bind_cols(d_locdat[,1])

rdl_nn <- function(sp, com){
  r.d1 %>% 
  filter(Species %in% {{sp}}) %>% select(!Species) %>%
  neighbours(which = mean) %>%
        unique() %>% 
        mean() %>% 
    as_tibble() %>% 
    add_column(com = {{com}})
}

nnamb <- rdl_nn(spamb, "Ambang")
nnbaw <- rdl_nn(spbaw, "Bawakaraeng")
nnbul <- rdl_nn(spbul, "Buliohuto")
nndak <- rdl_nn(spdak, "Dako")
nngan <- rdl_nn(spgan, "Gandangdewata")
nnkat <- rdl_nn(spkat, "Katopasa")
nnlat <- rdl_nn(splat, "Latimojong")
nnnok <- rdl_nn(spnok, "Nokilalaki")
nntor <- rdl_nn(sptor, "Torompupu")

rdlnn<- bind_rows(nnamb,nnbaw,nnbul,nndak,nngan,nnkat, nnlat, nnnok, nntor) %>% rename(c_nn_rda = value)
rdlnn
rm(nnamb,nnbaw,nnbul,nndak,nngan,nnkat, nnlat, nnnok, nntor)
```


### Estimate Simulated NN values 

All in one go. 
```{r}
nn_summary <- function( sp, com, list) {
  dlist <- list()
# Then estimate variance of 1000 random samples of species
for (i in 1:10){
  #THIS IS THE PART I CHANGED
  sp_ses <- subset(sp_ses, select = names(sp_ses) %in% {{list}})
  
    b <- picante::randomizeMatrix(sp_ses, null.model = "independentswap", iterations = 1000) %>% 
    as_tibble() %>% 
    bind_cols(com = c("Ambang", "Bawakaraeng", "Buliohuto", "Dako", "Gandangdewata", "Katopasa", "Latimojong", "Nokilalaki", "Torompupu")) %>% 
    pivot_longer(cols = -com, names_to = 'species') %>%
    filter(as.logical(value)) %>%
    select(-value) %>%
    filter(com == {{com}}) %>% 
    select(-com) %>%
    pull(species)
  
  dat1 <- r.d1 %>% 
  filter(Species %in% b) %>%
  select(!Species) %>% 
  neighbours(which = mean) %>%
    #unique() %>%
    mean() %>%
    as_tibble() %>% 
    add_column(com = {{com}})
  #
   dlist[[i]] <- dat1
  #return(b)
}
  bind_rows(dlist)
}

nn_summary2 <- function( sp, com, list) {
  dlist <- list()
# Then estimate variance of 1000 random samples of species
for (i in 1:15){
  #THIS IS THE PART I CHANGED
  sp_ses <- subset(sp_ses, select = names(sp_ses) %in% {{list}})
  
    b <- picante::randomizeMatrix(sp_ses, null.model = "frequency", iterations = 1000) %>% 
    as_tibble() %>% 
    bind_cols(com = c("Ambang", "Bawakaraeng", "Buliohuto", "Dako", "Gandangdewata", "Katopasa", "Latimojong", "Nokilalaki", "Torompupu")) %>% 
    pivot_longer(cols = -com, names_to = 'species') %>%
    filter(as.logical(value)) %>%
    select(-value) %>%
    filter(com == {{com}}) %>% 
    select(-com) %>%
    pull(species)
  
  dat1 <- r.d1 %>% 
  filter(Species %in% b) %>%
  select(!Species) %>% 
  neighbours(which = mean) %>%
    #unique() %>%
    mean() %>%
    as_tibble() %>% 
    add_column(com = {{com}})
  #
   dlist[[i]] <- dat1
  #return(b)
}
  bind_rows(dlist)
}

```

troubleshooting
Keeps hanging when I do the Bawakaraeng samples. Works for Ambang. It's something about the independentswap algorithm that hangs with the Bawa samples. 

```{r}
tt_baw <- subset(sp_ses, select = names(sp_ses) %in% dlist$Bawakaraeng)
tt_amb <- subset(sp_ses, select = names(sp_ses) %in% dlist$Ambang)

library(picante)

randomizeMatrix(tt_baw, null.model = "richness")

```


b <- picante::randomizeMatrix(sp_ses2, null.model = "independentswap", iterations = 1000) 


#%>% 
    as_tibble() %>% 
    bind_cols(com = c("Ambang", "Bawakaraeng", "Buliohuto", "Dako", "Gandangdewata", "Katopasa", "Latimojong", "Nokilalaki", "Torompupu")) %>% 
    pivot_longer(cols = -com, names_to = 'species') %>%
    filter(as.logical(value)) %>%
    select(-value) %>%
    filter(com == {{com}}) %>% 
    select(-com) %>%
    pull(species)



```{r}
nn_amb <-nn_summary( spamb, "Ambang", dlist$Ambang)
nn_baw <-nn_summary2( spbaw, "Bawakaraeng", dlist$Bawakaraeng)
nn_bul <-nn_summary2( spbul, "Buliohuto", dlist$Buliohuto)
nn_dak <-nn_summary( spdak, "Dako", dlist$Dako)
nn_gan <-nn_summary( spgan, "Gandangdewata", dlist$GandangDewata)
nn_kat <-nn_summary( spkat, "Katopasa", dlist$Katopasa)
nn_lat <-nn_summary( splat, "Latimojong", dlist$Latimojong)
nn_nok <-nn_summary( spnok, "Nokilalaki", dlist$Nokilalaki)
nn_tor <-nn_summary( sptor, "Torompupu", dlist$Torompupu)


nn_rand <- bind_rows(nn_amb, nn_baw, nn_bul, nn_dak, nn_gan, nn_kat, nn_lat, nn_nok, nn_tor) 
rm(nn_amb, nn_baw, nn_bul, nn_dak, nn_gan, nn_kat, nn_lat, nn_nok, nn_tor)
```

# Calculate SES
```{r}
rdlnn <- nn_rand %>% group_by(com) %>% 
  summarise(mean = mean(value),
            sd = sd(value)) %>% 
  as.data.frame() %>% 
  right_join(rdlnn, by = 'com') %>% 
  mutate(c_nnses_loc =  (c_nn_rda - mean) /sd) %>% 
  select(!c(mean, sd)) %>% 
  write_csv(here("Locomotion_Data", "C_NN_NNSES_Locomotor.csv"))
```
While we are here, we should add all the Locomotor results into one df
```{r}
read_csv(here("Locomotion_Data", "All_Locomotor_var.csv")) %>% 
  right_join(rdlnn, by = 'com') %>% 
  write_csv(here("Locomotion_Data", "All_Locomotor_var.csv"))
```

